\documentclass[12pt]{article}

\usepackage[top=1in,bottom=1in,left=1.25in,right=1.25in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{url}
\usepackage{float}

\hypersetup{
    colorlinks=true,
    linkcolor=blue!70!black,
    citecolor=green!60!black,
    urlcolor=blue!70!black,
}

\lstset{
    basicstyle=\ttfamily\small,
    breaklines=true,
    frame=single,
    backgroundcolor=\color{gray!10},
}

\title{\textbf{Closed-Loop Streaming Synthesis}\\[2pt]
\textbf{Bounded-Drift, Arbitrary-Length Audio--Video Generation}\\
\textbf{by Treating Chunk Hand-off as Feedback Control}}

\author{Aleksander Majda\\
}

\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
Generating arbitrarily long videos with diffusion transformers requires splitting the
temporal dimension into overlapping chunks.  Naive open-loop chunk-streaming
accumulates exposure-bias drift: each chunk is conditioned on the previously
generated latent, compounding distributional errors and causing scene collapse or
grain amplification after a few hundred frames.  We present
\textbf{Closed-Loop Streaming Synthesis (CLSS)}, a suite of four post-denoising
corrections that close the feedback loop between successive chunks without modifying
the transformer weights: calibrated context re-noising, per-channel EMA-tracked
AdaIN, frequency-band soft shrinkage, and a dynamic anchor bank.  CLSS is
implemented as a ComfyUI custom-node pipeline targeting LTX-2.3 22B (a 44\,GB
audio-video diffusion transformer) on consumer 16\,GB VRAM hardware via GGUF
4-bit quantisation and CPU block-streaming.  Generation is driven by a
reference-parity multi-modal guider (split per-modality classifier-free
guidance, modality-isolation guidance, and spatiotemporal guidance via a
value-passthrough self-attention skip) that correctly handles ComfyUI's
packed audio-video latent representation, and all streaming noise is seeded
for bit-reproducible runs.  A two-stage pipeline generates a draft
audio-video via CLSS streaming and then refines it using a 3-step
distilled-LoRA schedule at $2\times$ spatial resolution.

We report matched text-to-video (T2V) and image-to-video (I2V) experiments:
single-scene, $\approx53$-second clips generated as ten chunks
($\text{new\_lf}=16$, $\text{overlap}=8$, per-chunk phase-jittered) under an
identical seed and guidance stack (split per-modality CFG 4.0 video / 7.0
audio, STG 1.0 on both modalities at block 28, rescale 0.70; three transformer
passes per step), differing only in the presence of a guide image.  Stage~1
holds video boundary cosine similarity on a rising trajectory in I2V
($0.79\to0.98$) and a flat first-to-last trajectory with a mid-run floor in
the dynamic-content T2V run ($0.796\to0.790$, floor $0.469$ at chunk~5); a
two-band spatial detail anchor holds the high-frequency energy share flat
across the full run in both modes ($0.509\to0.509$ I2V, $0.486\to0.486$ T2V),
closing the progressive-softening channel, and a reference-exact RMS anchor
holds audio loudness to its chunk-1 level throughout ($\pm5\%$).  The
per-chunk loudness-envelope repetition (the ``metronome'' of earlier
chunked-audio runs) is diagnosed as a \emph{fixed point of the constant-shape
chunk grid}: with a constant overlap, every continuation chunk denoises an
identical window and keeps the same phase of the model's window arc, so the
same loudness gesture recurs each chunk.  It is eliminated chunk-natively by a
per-chunk overlap phase-jitter --- cycling the overlap through
$[\text{full},\,\text{half},\,\tfrac34]$ of its configured value so no two
consecutive chunks share a window shape --- which preserves arbitrary-length
streaming and introduces no audio/video offset; with the phase lock broken
structurally, the previously harmful audio SLB is restored as the
content-continuity carrier and the RMS anchor keeps energy stability.  Against
earlier matched runs, the loudness-envelope correlation drops from a sustained
$0.76$--$0.96$ to $\le0.19$ at every hand-off ($-0.51$--$0.19$ across both
runs), audio boundary similarity rises from
$0.07$--$0.53$ to a $0.85$--$0.92$ typical band ($0.619\to0.918$ first-to-last
in I2V, $0.849\to0.916$ in T2V), and both phase-lock detectors read fully
scattered (peak mode covering $1/10$ chunks in each run).  Audio
high-frequency energy growth, previously unbounded, is closed in T2V
($0.885\to0.772$) and reduced to a mild residual in I2V ($0.881\to1.047$).
Stage~2 ($2\times$ resolution, 3-step distilled refinement in four
windows) refines video against frozen Stage-1 audio, with its own per-window
detail anchor referenced to the upscaled Stage-1 slice; end-of-window fidelity
to Stage-1 structure stays at $0.91$--$0.97$ (I2V).  Total generation time is
$\approx96$--$97$ minutes per clip on a single 16\,GB GPU.
\end{abstract}

%--------------------------------------------------------------------------
\section{Introduction}
\label{sec:intro}
%--------------------------------------------------------------------------

Modern video diffusion transformers operate on patchified latent representations
where temporal resolution is down-scaled $8\times$ relative to pixel frames.
Fitting a 30-second clip (81,840 tokens at $22\times40$ spatial) into a single
forward pass requires very large GPUs.  The standard remedy is \emph{temporal
chunking} via a Streaming Latent Buffer (SLB): generate the video in short
overlapping segments, conditioning each on the previous denoised output.
Section~\ref{sec:background} reviews this mechanism and the exposure-bias
problem it introduces.

CLSS closes the feedback loop between chunks by applying five lightweight
post-denoising corrections that together bound the closed-loop gain below one,
preventing drift from accumulating without modifying the transformer weights.
The corrections are applied purely at the boundary between chunks and add
negligible computational overhead.

\paragraph{Contributions.}
\begin{enumerate}[leftmargin=*,noitemsep]
\item Five closed-loop correction modules for temporal chunk streaming:
      calibrated context re-noising, EMA-tracked per-channel AdaIN,
      frequency-band soft shrinkage, a dynamic anchor bank, and a two-band
      spatial detail anchor that closes the progressive-softening channel the
      one-sided shrinkage leaves open
      (Sections~\ref{sec:renoise}--\ref{sec:detail}).
\item A per-chunk \emph{overlap phase-jitter} mechanism that breaks the
      fixed-point repetition of chunked autoregressive audio at the chunk-grid
      level --- cycling the per-chunk overlap through
      $[\text{full},\,\text{half},\,\tfrac34]$ of its configured value so no
      two consecutive chunks share a window shape --- together with the audio
      SLB it makes safe to restore as the content-continuity carrier, all
      while preserving arbitrary-length streaming and exact audio/video
      proportionality (Section~\ref{sec:jitter}).
\item A linear stability analysis of the feedback loop in latent space,
      including an empirical per-chunk gain measurement protocol
      (Section~\ref{sec:stability}).
\item A memory-efficient two-stage pipeline for LTX-2.3 22B on 16\,GB VRAM
      using GGUF 4-bit quantisation and CPU block-streaming
      (Section~\ref{sec:impl}).
\item A reference-parity multi-modal guider for ComfyUI (split per-modality
      CFG, modality-isolation guidance, and STG via value-passthrough
      self-attention skip) that correctly handles ComfyUI's packed audio-video
      latent representation (Section~\ref{sec:guider}).
\item ComfyUI custom nodes implementing the full pipeline with seeded,
      bit-reproducible streaming noise and per-chunk reproducibility telemetry:
      unconditional settings dumps, per-frame origin/layout drift event tables,
      and a phase-lock repetition detector (Sections~\ref{sec:nodes},
      \ref{sec:failures}).
\item Matched $\approx53$-second T2V and I2V generations, identical seed and
      guidance stack, streamed as ten chunks each, isolating the effect of
      visual conditioning on continuity and drift, and resolving the
      loudness-envelope repetition earlier runs exhibited: diagnosed as a
      fixed point of the constant-shape chunk grid --- after being shown
      immune to every conditioning- and guidance-level intervention, which is
      exactly what motivated the grid-level diagnosis --- and eliminated by
      the overlap phase-jitter plus the restored audio SLB
      (Sections~\ref{sec:experiments}, \ref{sec:jitter},
      \ref{sec:failures}).
\end{enumerate}

%--------------------------------------------------------------------------
\section{Background}
\label{sec:background}
%--------------------------------------------------------------------------

\subsection{LTX-2.3 Architecture}
LTX-2.3 is a 22-billion-parameter diffusion transformer for joint audio-video
synthesis.  It operates on a latent space with an $8\times$ temporal downscale
(video VAE, causal) and a $160\times4\times$ audio downscale (audio VAE,
16\,kHz, hop length 160, compression factor 4), yielding a video latent rate
of $25/8 = 3.125$ lf/s and an audio latent rate of $16000/(160\times4)=25.0$
lf/s.  The model accepts interleaved video and audio tokens together with
Gemma-3 text embeddings and is trained with flow-matching on the
rectified-flow schedule.

\subsection{Streaming Latent Buffer (SLB)}
The SLB provides temporal continuity in chunk streaming.  When generating
chunk $N$, the last $\text{overlap\_lf}$ latent frames from chunk $N-1$ are
prepended to the new chunk's latent, and the denoiser is conditioned on them
at noise level $\tau_c$:
\begin{equation}
\tilde{L}_{\text{overlap}} = (1-\tau_c)\,\hat{L}_{\text{overlap}} + \tau_c\,\varepsilon,
\quad \varepsilon \sim \mathcal{N}(0, I)
\label{eq:renoise}
\end{equation}
Setting $\tau_c=0$ yields maximal continuity but maximal drift risk;
$\tau_c=1$ decouples the chunks entirely.  In LTX's framework this is
implemented as \texttt{VideoConditionByLatentIndex} with
$\text{strength}=1-\tau_c$.

\paragraph{Implementation note: masked timestep, not a one-shot draw.}
Eq.~\eqref{eq:renoise} describes the target distribution of the overlap
context, but the sampler does not literally draw $\varepsilon$ once and hand
the model a truncated schedule from $\tau_c$.  Tracing the actual mechanism
(\texttt{ComfyBaseModel.process\_timestep} for the LTX model, which the
\texttt{noise\_mask}/\texttt{strength} produced by
\texttt{VideoConditionByLatentIndex} feeds into) shows that the per-token
timestep supplied to the transformer at every sampling step $t$ is
$\tau_{\text{eff}} = (1-\text{strength})\cdot\sigma_t = \tau_c\,\sigma_t$ for
overlap tokens, versus $\sigma_t$ for the rest of the sequence --- a
\emph{persistent} per-step rescaling of the global noise schedule, applied at
every step, not a single noise-injection event applied once before an
otherwise-standard remaining schedule. For a \emph{linear} (rectified-flow)
interpolation path, $x_t = (1-t)x_0 + t\varepsilon$, these two descriptions
coincide exactly: scaling every step's effective time by a constant factor
$\tau_c$ is algebraically identical to drawing $x_{\tau_c}$ once via
Eq.~\eqref{eq:renoise} and continuing the \emph{same} linear ODE from
$\tau_c$ down to $0$. LTX-2.3 is trained with a rectified-flow objective
(Section~\ref{sec:background}), so the equivalence holds for this model; it
would not hold in general for a non-linear (e.g.\ cosine or EDM) noise
schedule, where per-step time-rescaling and one-shot truncated-schedule
sampling are not interchangeable.

\subsection{Exposure Bias in Streaming Diffusion}
Let $\hat{L}_N$ be the denoised latent of chunk $N$ and
$f_\theta(\cdot\mid\hat{L}_{N-1})$ the denoising operator conditioned on the
previous chunk.  In open-loop streaming:
\begin{equation}
\hat{L}_N = f_\theta(\hat{L}_{N-1} + \varepsilon_N)
\end{equation}
The transformer was trained on latents drawn from the data distribution, but at
inference it receives denoised latents from prior chunks, which lie
off-manifold relative to its training distribution.  Any distributional shift
$\delta_N = \hat{L}_N - L_N^*$ (where $L_N^*$ is the ``on-manifold'' latent
for the same content) is in general amplified by the open-loop gain of the
denoising process.  Formally, if $g = \|\partial f_\theta / \partial L\|$
evaluated at $L_{N-1}^*$, then $\|\delta_{N+1}\| \approx g\|\delta_N\|$.
When $g > 1$ this gives $\|\delta_N\| \sim g^N \to \infty$.

In practice $g$ is not a global constant: it depends on the noise level
schedule, step count, guidance strength, and the spectral content of the
latent.  Section~\ref{sec:stability} describes how $g$ is estimated
empirically per chunk via a perturbation measurement.

%--------------------------------------------------------------------------
\section{Closed-Loop Streaming Synthesis}
\label{sec:clss}
%--------------------------------------------------------------------------

CLSS adds five closed-loop correction modules that together bound the error
accumulation by ensuring $\rho_{\text{closed}} = g \cdot (1-\beta)\cdot(1-\tau_c) < 1$.

\subsection{Calibrated Context Re-Noising}
\label{sec:renoise}

The overlap latent fed as context to chunk $N$ is re-noised to level $\tau_c$
via Eq.~\eqref{eq:renoise}.  This forces the denoiser to actively re-project
the boundary context onto the data manifold rather than accepting it verbatim,
partially correcting accumulated drift in the SLB.

In practice $\tau_c=0.05$ provides a strong temporal constraint
(boundary cosine similarity $>0.97$) while allowing enough distributional
repair to prevent drift accumulation.  Larger values ($\tau_c=0.20$, as
suggested by some prior work) loosen the constraint too much for 22B GGUF
streaming, causing visible motion discontinuities.

\subsection{EMA-Tracked Per-Channel AdaIN}
\label{sec:adain}

A slow exponential moving average (EMA) with rate $\lambda \approx 0.10$
tracks per-channel mean $\mu_c$ and standard deviation $\sigma_c$ across chunks:
\begin{align}
\mu_c^{(N)} &= (1-\lambda)\,\mu_c^{(N-1)} + \lambda\,\hat\mu_c^{(N)} \\
\sigma_c^{(N)} &= (1-\lambda)\,\sigma_c^{(N-1)} + \lambda\,\hat\sigma_c^{(N)}
\end{align}
where $\hat\mu_c^{(N)}, \hat\sigma_c^{(N)}$ are the per-channel statistics of
chunk $N$'s new frames.  After generation, the overlap region is dropped and
\emph{only the new frames} $L_N^{\text{new}}$ (Algorithm~\ref{alg:clss},
line~5) are blended toward the EMA reference via AdaIN with blend factor
$\beta$:
\begin{equation}
\tilde{L}_N^{\text{new}} = (1-\beta)\,L_N^{\text{new}} + \beta\;\text{AdaIN}(L_N^{\text{new}} \to \mu^{(N-1)}, \sigma^{(N-1)})
\end{equation}
The overlap region itself is never re-touched by AdaIN --- it was already
corrected as \emph{previous} chunk's $L_{N-1}^{\text{new}}$ before being pushed
to the SLB.  This suppresses fast per-chunk statistical drift while allowing
slow intentional scene evolution (lighting changes, colour grading) to pass
through.

Two safety caps prevent over-correction:
\begin{itemize}[noitemsep]
\item \textbf{Sigma max drift}: the EMA $\sigma_c$ is clamped to at most
  $(1+\Delta)\times\sigma_c^{(0)}$ (default $\Delta=0.05$), preventing AdaIN
  from amplifying late-chunk residual noise.
\item \textbf{AdaIN max amplification}: per-channel upward scaling is capped
  at $1.2\times$ the current chunk's std (default), preventing AdaIN from
  boosting noise in channels that have become quiet.
\end{itemize}

\subsection{Frequency-Band Soft Shrinkage}
\label{sec:shrink}

The latent is decomposed into $B=4$ frequency bands via 3-D FFT along
the (frame, height, width) axes.  Each band $b$ receives a continuous gain:
\begin{equation}
g_b^{(c)} = \min\!\left(1,\; \left(\frac{E_{\text{ref},b}^{(c)}}{E_{b}^{(c)}}\right)^{\!\gamma_b}\right) \in (0,1]
\label{eq:gain}
\end{equation}
where $E_b^{(c)}$ is the mean squared amplitude of band $b$ in channel $c$,
$E_{\text{ref},b}^{(c)}$ is the corresponding EMA reference, and
$\gamma_b$ is the per-band shrinkage exponent.

Only bands with excess energy relative to their EMA are attenuated.  Bands with
$\gamma_b = 0$ (the DC band) are never attenuated.  Default exponents:
$\boldsymbol\gamma = (0.0,\,0.05,\,0.2,\,0.3)$, which are conservative enough
to preserve scene structure while suppressing temporal flicker.

The EMA is updated with the \emph{corrected} (post-gain) energies, not the raw
ones, so the reference tracks intentional scene content rather than accumulated
error.

\subsection{Dynamic Anchor Bank}
\label{sec:anchor}

A small bank of $M \le 8$ keyframe anchors provides long-range visual identity
conditioning.  The bank is seeded from the \emph{last} frame of chunk 1 (not
the first) and updated when two consecutive chunks trigger a scene-change
signal (cosine similarity below threshold $\rho_a=0.78$ for $P=2$ consecutive
chunks).  Additionally, a \emph{forced insertion} every $F_a$ chunks
($\text{chunk\_index} \bmod F_a = 0$, chunk~1 always seeds regardless) prevents
bank stagnation on visually stable sequences where the similarity threshold is
never triggered.  The reference default is $F_a=5$; the ComfyUI node
auto-derives $F_a = \max(2, \min(5, \lceil\text{num\_chunks}/4\rceil))$, giving
$F_a=3$ for the ten-chunk experiments in Section~\ref{sec:experiments}.

Anchors are retrieved via cosine similarity and injected as
\texttt{VideoConditionByKeyframeIndex} at frame index 0 of the current chunk.
Anchors too similar to the current overlap (${\rm sim} > 0.85$) are skipped to
avoid duplicating the SLB conditioning.  LRU eviction discards the least recently
used anchor when the bank is full.

\subsection{Two-Band Spatial Detail Anchoring}
\label{sec:detail}

The shrinkage of Section~\ref{sec:shrink} is deliberately one-sided
(Eq.~\eqref{eq:gain} only ever attenuates), and this asymmetry has a measured
long-run consequence: low-band energy inflates while high bands are only ever
shrunk, so the \emph{high-frequency share} of latent energy falls monotonically
--- $+19.6\%$ band-0 inflation over seven chunks in one measured run, with the
uncapped band EMA itself drifting upward and legitimising the excess.  Nothing
in the shrinkage loop can \emph{restore} band energy, and the perceptual result
is progressive detail loss.

The detail anchor closes exactly this channel.  Each frame is split into a
spatial low band (a $3\times3$ average pool over the latent grid) and its
high-band residual, and the mean squared energy of each band is equalised
toward a \emph{fixed} scene-first reference (captured at chunk~1, re-baselined
on scene change) with symmetric per-chunk gains:
\begin{equation}
g_{\rm lo} = \Big(\tfrac{E_{\rm lo}^{\rm ref}}{E_{\rm lo}}\Big)^{1/2}
\;\text{clamped to } [0.90, 1.10], \qquad
g_{\rm hi} = \Big(\tfrac{E_{\rm hi}^{\rm ref}}{E_{\rm hi}}\Big)^{1/2}
\;\text{clamped to } [0.90, 1.12]
\label{eq:detail}
\end{equation}
Unlike the shrinkage EMA, the reference here does not track the output ---
drift cannot legitimise itself --- and unlike the shrinkage gains, these are
symmetric: lost high-band energy is restored, not merely excess removed.  The
per-chunk clamp bounds the correction so a genuine scene change cannot be
fought harder than $\pm10$--$12\%$ per chunk, and a $\pm0.5\%$ dead-band makes
the module a strict no-op when energies already match.  The same mechanism runs
per-window in Stage~2, referenced there to the upscaled Stage-1 slice of the
same window (Section~\ref{sec:twostage}).  In the reported runs it holds the
Stage-1 high-frequency share flat end-to-end ($0.509\to0.509$ I2V,
$0.486\to0.486$ T2V; Section~\ref{sec:experiments}).

\subsection{Stability Analysis}
\label{sec:stability}

The AdaIN blend (Section~\ref{sec:adain}) and context re-noising
(Section~\ref{sec:renoise}) together reduce the magnitude of any per-chunk
latent perturbation by a factor $(1-\beta)(1-\tau_c)$ before it reaches the
next chunk's denoiser.  This gives the \emph{loop gain}:
\begin{equation}
\rho_{\text{loop}} = (1-\beta)\cdot(1-\tau_c)
\label{eq:rholoop}
\end{equation}
The combined closed-loop gain, accounting for the model's open-loop
amplification $g$, is:
\begin{equation}
\rho_{\text{closed}} = g \cdot \rho_{\text{loop}}
\end{equation}
Bounded drift requires $\rho_{\text{closed}} < 1$.  With $\beta=0.40$ and
$\tau_c=0.05$, $\rho_{\text{loop}} = 0.57$, providing $\approx43\%$ gain
reduction per chunk before accounting for $g$.

\paragraph{Why the two factors multiply.}  $(1-\tau_c)$ and $(1-\beta)$ act on
disjoint tensor regions at different points in the cycle --- $(1-\tau_c)$ on
the \emph{overlap} region when it is \emph{read} as context
(Section~\ref{sec:renoise}), $(1-\beta)$ on the \emph{new-frame} region when it
is \emph{written} as output (Section~\ref{sec:adain}, and see the corrected
notation there: AdaIN never re-touches the overlap).  This is not two
attenuators applied to the same signal at the same place; it is two
attenuators the same error signal passes through exactly once per loop
iteration: a perturbation in chunk $N$'s output is written with gain
$(1-\beta)$ (since AdaIN is applied uniformly across $L_N^{\text{new}}$,
including the tail frames that become the next SLB), then read back with gain
$(1-\tau_c)$ once it becomes chunk $N{+}1$'s overlap context. For a
linear, time-invariant loop this is exactly the standard construction of a
loop gain from attenuators in series --- the product is valid \emph{because}
each attenuator sits on the one path the error must traverse per cycle, not
because they act on the same coefficients. What Eq.~\eqref{eq:rholoop} does
not capture is any cross-term where the correction strength itself depends on
chunk content (e.g.\ the AdaIN amplification cap, Section~\ref{sec:adain},
engages non-uniformly); that content-dependence is exactly why $g$ cannot be
folded into a single constant either (below).

Note that Eq.~\eqref{eq:rholoop} is a first-order approximation that treats the
two corrections as independent multiplicative attenuators.  In practice $g$ is
not constant: it depends on the step count, guidance strength, noise schedule,
and the spectral properties of the current latent.  The analysis therefore
provides a stability condition rather than a precise quantitative bound.  The
frequency-band shrinkage (Section~\ref{sec:shrink}) provides additional spectral
attenuation beyond $\rho_{\text{loop}}$, especially in high-frequency bands, but
is not included in the linear gain model because its contribution is content- and
chunk-dependent.

\paragraph{Hyperparameter Choices.}
$\beta=0.40$ is the largest value that preserves scene-change responsiveness in
practice: at $\beta\geq0.5$ slow colour shifts accumulate due to excessive EMA
anchoring.  $\tau_c=0.05$ is a conservative re-noising level that maintains
high boundary similarity ($>0.97$) while partially correcting SLB distribution
shift; larger values ($\tau_c\geq0.20$) cause visible motion discontinuities on
22B streaming.  Together they yield $\rho_{\text{loop}}=0.57$, which empirically
provides adequate margin given the band-energy-growth proxy for $g$ discussed
in Section~\ref{sec:discussion} (note: not the $g_{\rm SLB}$ perturbation
measurement below, which was not exercised in the reported runs).
$\lambda=0.10$ (EMA
rate) was chosen to respond to gradual scene evolution without over-weighting
individual chunks; $\boldsymbol\gamma=(0.0,\,0.05,\,0.2,\,0.3)$ are
conservative exponents that attenuate only bands with clear excess energy.

\paragraph{Per-Chunk Gain Measurement.}
$g$ is measured empirically by running a second denoising pass with a slightly
perturbed overlap latent $\tilde{L}_{\text{overlap}} + \delta$
($\|\delta\|_F = \epsilon\,\|\tilde{L}_{\text{overlap}}\|_F$, $\epsilon=0.01$)
and comparing the output perturbation to the input:
\begin{equation}
g_{\rm SLB} = \frac{\|\Delta_{\rm output}^{\rm SLB}\|_F}{\|\delta\|_F}
\label{eq:gslb}
\end{equation}
where $\Delta_{\rm output}^{\rm SLB}$ is restricted to the last
$\text{overlap\_lf}$ new frames---the portion that becomes the next chunk's
SLB.  This measures sensitivity of the boundary output to boundary input
perturbations, which is the relevant quantity for SLB-mediated drift
propagation.  It does not capture drift arising from other channels (e.g.,
prompt conditioning or attention to non-overlap frames), so $g_{\rm SLB}$
is a lower bound on the true open-loop gain.

The \texttt{measure\_g} config field existed from the start, but --- caught
only when this was checked directly rather than assumed --- no code actually
implemented Eq.~\eqref{eq:gslb} behind it; the flag was a documented no-op,
hardcoded off with no node-level toggle.  This has since been implemented: a
second denoising pass with a perturbed overlap latent, holding the noise
sample and every other conditioning input fixed, comparing the raw
(pre-AdaIN/shrink) output tail against the unperturbed pass.  It is verified
at the tensor level --- the perturbation is confined exactly to the overlap
region, the norm-ratio formula recovers a known injected gain in a synthetic
test --- but \textbf{was not enabled in either experiment reported in
Section~\ref{sec:experiments}}, both of which predate the implementation and
ran with \texttt{measure\_g=False} regardless; consequently no $g_{\rm SLB}$
value appears in any results table here, and the measurement itself is
untested against a live transformer forward pass.  The $g\approx1.03$--$1.05$
figures in Section~\ref{sec:discussion} are a \emph{different}, informal proxy
---the ratio of measured band-3 latent energy growth to its EMA
reference---not an instance of Eq.~\eqref{eq:gslb}.  The two should not be
conflated: the band-energy proxy reflects unshrunk spectral drift under the
full correction stack as actually run, while $g_{\rm SLB}$ would isolate the
transformer's own sensitivity to a boundary perturbation, holding every
correction fixed.  Executing \texttt{measure\_g=True} on a future run is the
direct way to close this gap; it is listed as an open item in
Section~\ref{sec:limitations}.

%--------------------------------------------------------------------------
\section{Algorithm}
\label{sec:algorithm}
%--------------------------------------------------------------------------

Algorithm~\ref{alg:clss} summarises the per-chunk CLSS procedure.

\begin{algorithm}[H]
\caption{CLSS per-chunk generation}
\label{alg:clss}
\begin{algorithmic}[1]
\Require Config: $\tau_c, \beta, \lambda, \boldsymbol\gamma$; state: SLB, EMA, anchor bank
\State $L_{\text{ov}} \leftarrow$ SLB.read()  \Comment{may be empty for chunk 0}
\State $\tilde{L}_{\text{ov}} \leftarrow (1-\tau_c)\,L_{\text{ov}} + \tau_c\,\varepsilon$ \Comment{Eq.~\eqref{eq:renoise}; Sect.~\ref{sec:renoise}}
\State $A \leftarrow$ anchor\_bank.retrieve(top-$m$ by cosine sim) \Comment{Sect.~\ref{sec:anchor}}
\State $L_N \leftarrow$ Denoise($\tilde{L}_{\text{ov}},\, A,\, \text{prompt}_N$)
\State $L_N^{\rm new} \leftarrow L_N[\text{overlap\_lf}:]$ \Comment{drop overlap region}
\State $L_N^{\rm new} \leftarrow$ AdaIN\_blend($L_N^{\rm new}$, EMA, $\beta$) \Comment{Sect.~\ref{sec:adain}}
\State $L_N^{\rm new} \leftarrow$ band\_soft\_shrink($L_N^{\rm new}$, band\_EMA, $\boldsymbol\gamma$) \Comment{Sect.~\ref{sec:shrink}}
\State $L_N^{\rm new} \leftarrow$ detail\_anchor($L_N^{\rm new}$, $E^{\rm ref}_{\rm lo/hi}$) \Comment{Eq.~\eqref{eq:detail}; Sect.~\ref{sec:detail}}
\State EMA.update($L_N^{\rm new}$, $\lambda$); band\_EMA.update($L_N^{\rm new}$, $\lambda$)
\State anchor\_bank.update(last frame of $L_N^{\rm new}$) \Comment{Sect.~\ref{sec:anchor}}
\State SLB.push($L_N^{\rm new}[-\text{overlap\_lf}:]$)
\State \Return $L_N^{\rm new}$
\end{algorithmic}
\end{algorithm}

%--------------------------------------------------------------------------
\section{Implementation}
\label{sec:impl}
%--------------------------------------------------------------------------

\subsection{Memory Budget for 16\,GB VRAM}
\label{sec:memory}

LTX-2.3 22B in BF16 occupies $\approx44$\,GB.  Three complementary strategies
fit it within 16\,GB VRAM:

\begin{enumerate}[leftmargin=*,noitemsep]
\item \textbf{GGUF 4-bit quantisation} (Q4\_K\_S): reduces the on-disk size
  to $\approx11$\,GB.  Dequantization to BF16 at load time requires
  $\approx44$\,GB of pinned CPU RAM.
\item \textbf{CPU block-streaming}: all transformer blocks reside in pinned
  CPU RAM; only 2 blocks are resident on GPU at a time ($\approx5$\,GB
  model weights on GPU), with the next block pre-fetched asynchronously
  via a dedicated CUDA stream.
\item \textbf{Temporal chunking (CLSS)}: latent memory is $O(\text{overlap\_lf})$
  instead of $O(\text{total\_frames})$.  Processed chunk latents are immediately
  offloaded to CPU after each chunk.
\end{enumerate}

Combined peak VRAM budget at $512\times768$ resolution:
\begin{center}
\begin{tabular}{lr}
\toprule
Component & Peak VRAM \\
\midrule
Model blocks (2 $\times$ BF16, streaming) & $\approx5$\,GB \\
Activations + latents (per chunk) & $\approx4$\,GB \\
VAE / text encoder (loaded/freed) & $\approx2$\,GB \\
\midrule
\textbf{Total peak} & $\approx11$\,GB \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Two-Stage Pipeline}
\label{sec:twostage}

\paragraph{Stage 1 (Open-resolution streaming).}
CLSS streaming generates the full video at a coarse latent resolution
($H_L \times W_L$ latent grid, typically $11\times20$ for $704\times512$ output).
Each chunk runs the full 20--30-step LTX scheduler.  CLSS corrections are applied
between chunks as per Algorithm~\ref{alg:clss}.

\paragraph{Stage 2 (Distilled-LoRA refinement).}
Stage 1 operates at $704\times512$ output resolution and 20 denoising steps,
which is sufficient for temporal structure and scene content but produces
visible quantisation artefacts and reduced texture detail, particularly after
GGUF 4-bit dequantisation at the low-frequency latent scale.  Stage 2 addresses
this by upsampling and refining the output.

The Stage 1 output is spatially upsampled $2\times$ by
\texttt{LTXVLatentUpsampler}, yielding a $22\times40$ latent grid corresponding
to $1408\times1024$ pixel resolution.  Stage 2 then refines the full video in
temporal chunks using a 3-step distilled-LoRA schedule with initial noise level
$\sigma_0 \approx 0.909$.  Each chunk's new frames are seeded from the upscaled
Stage 1 latent with $\sigma_0$-scaled noise:
\begin{equation}
x_{\text{start}} = \sigma_0\,\varepsilon + (1-\sigma_0)\,L_N^{\text{S1}}
\end{equation}
This formulation anchors Stage 2 to the coarse temporal structure produced by
Stage 1---preserving scene layout, motion trajectories, and chunk boundaries
established by CLSS---while allowing the 3-step refinement to add local
high-frequency detail.  Stage 1 alone could in principle be generated at
$2\times$ resolution, but this would quadruple token count and exceed VRAM
budget under CPU block-streaming.

Key differences from Stage 1:
\begin{itemize}[noitemsep]
\item AdaIN and spectral-shrinkage corrections are \emph{disabled}: Stage 2
  refinement is structurally anchored to the S1 latent, so distributional
  drift correction is unnecessary.
\item The detail anchor (Section~\ref{sec:detail}) \emph{does} run, per
  window, with the reference recomputed from that window's upscaled Stage-1
  slice rather than carried from a first-window EMA.  The 3-step distilled
  refinement systematically adds spatial high-frequency energy relative to
  its Stage-1 seed, and without the anchor this excess compounds across the
  window chain as end-of-run softening of the refined output relative to
  Stage-1 structure.  Per-window re-referencing means the correction cannot
  accumulate: each window is equalised to its own source.
\item A global pre-generated noise field is sliced per chunk
  (\texttt{\_SlicedNoise}) to prevent grain seams at chunk boundaries---a
  single coherent noise tensor ensures that the per-chunk noise samples tile
  seamlessly when concatenated.
\item Audio is \emph{frozen}: the Stage-1 audio latent is passed through
  unchanged (denoise mask 0) and only video tokens are refined, with the
  frozen audio serving as cross-modal context.  Re-rendering audio in Stage-2
  windows was measured to re-seam it at every window boundary; freezing keeps
  the audio timeline bit-identical to Stage~1
  (\texttt{frozen\_verify\_sim}=1.0 per window).
\end{itemize}

\subsection{Audio Streaming}
\label{sec:audio}

Audio and video share the same temporal chunk boundaries.  Audio length
accounting is anchored to \emph{pixel time}: the causal video VAE maps a
chunk of $\text{new\_lf}$ latent frames to $(\text{new\_lf}-1)\cdot 8+1$
pixel frames for the first chunk of a sequence and $\text{new\_lf}\cdot 8$
pixel frames for every continuation chunk.  The audio rate is taken from the
chunk template, $r = \text{new\_af} / \big((\text{new\_lf}-1)\cdot 8+1\big)$
audio frames per pixel frame, and the SLB length follows the same rate:
\begin{equation}
\text{overlap\_af} = \text{round}\!\left(\text{overlap\_lf}\cdot 8 \cdot r\right)
\end{equation}
With $\text{overlap\_lf}=8$ and the 13-lf/102-af template this gives
$\text{overlap\_af}=67$.  (An earlier per-chunk accounting ignored the
causal first-frame discount, undercounting every continuation chunk by
$\approx0.28$\,s and desynchronising audio from video by $\approx2$\,s over
seven chunks; the pixel-time ledger above eliminates the drift exactly.)
The effective video overlap is additionally clamped to $\text{new\_lf}$: the
SLB can never carry more frames than a chunk produces, and unclamped values
were measured to silently discard motion at every seam.

\paragraph{Continuity via the audio SLB, restored.}
Audio continuity is carried by two complementary conditioning paths.  The
first is an audio analogue of the video SLB: the previous chunk's audio tail
is seeded into the overlap region at $\tau_c$, so the model \emph{hears} what
it continues rather than inferring it from context.  The buffer is stored at
the configured maximum length and each chunk slices the tail matching its
jittered overlap (Section~\ref{sec:jitter}); the freeze is verified
numerically every chunk (\texttt{SLB honored}$=1.0000$ in both reported
runs).  The second path is a reference-audio window (\texttt{ref\_audio}
tokens at negative temporal RoPE) taken from the previous chunk's pre-overlap
tail and passed \emph{clean and at full length} (67\,af $\approx2$\,s,
decoupled from the video overlap; an implicit coupling to
$\text{overlap\_af}$ starved it at small overlaps and measurably collapsed
within-chunk audio coherence from 0.91 to 0.27).  The SLB path has a
confounded history worth recording.  Under a \emph{constant} overlap it was
measured harmful and disabled: the buffer froze each chunk's loudest tail
into the next chunk's opening, compounding into high-frequency runaway
($1.02\to1.51$ over ten chunks) and raw-RMS runaway that the energy anchor
then fought with growing corrections.  That left \texttt{ref\_audio} as the
only carrier, which proved far too weak alone --- boundary cosine
$0.07$--$0.53$ in I2V, with every chunk re-inventing its audio and speech
rendered unintelligible.  In retrospect the SLB was blamed for a loop that
lived in the chunk grid, not in the buffer: its ``harm'' was feeding the
phase-locked fixed point analysed in Section~\ref{sec:jitter}.  With the
phase lock broken structurally by the overlap jitter, the same SLB shows no
runaway (T2V \texttt{aud\_hf} $0.885\to0.772$ over the run) and lifts
boundary similarity to a $0.85$--$0.92$ typical band.  The division of labour
is: \textbf{jitter = anti-repetition, audio SLB = content continuity, RMS
anchor = energy stability}.  Perturbing the reference window itself ---
blending in noise, shrinking its length over chunks, flattening its loudness
envelope --- was each tested live against the repetition and none helped (the
energy-injecting variants added audible hiss); those failures were what
redirected the search from conditioning \emph{values} to the window
\emph{shape} (Section~\ref{sec:failures}).  The clean full-length reference
remains the measured optimum.

\paragraph{Reference-exact RMS anchoring.}
Un-anchored streaming audio is a divergent loop: runs were measured with RMS
growing $+67\%$ and low-mid spectral bands tripling over ten chunks.  A
per-chunk anchor corrects the new audio's global RMS toward an EMA target
whose drift from the chunk-1 reference (computed onset-excluded) is
hard-capped at $\pm5\%$ (the same $\Delta_\sigma$ used for the video EMA),
before the chunk's tail is fed forward as the next reference window.
Anchoring \emph{before} feed-forward is what keeps the recursion safe at any
sequence length.  In the T2V run this anchor absorbs raw per-chunk loudness
excursions of $0.734$--$0.842$ against a chunk-1 onset-excluded reference of
$0.8404$, holding output RMS at $0.806$--$0.840$ (largest correction gain
$1.12$, chunk~3); in I2V it absorbs raw excursions of $-9\%$/$+19\%$
($0.511$--$0.663$ against a reference of $0.5589$), holding output at
$0.554$--$0.587$ with corrections of up to $14\%$ downward
(Sections~\ref{sec:t2v_audio}, \ref{sec:i2v_audio}).  On multi-scene
runs the anchor is re-baselined at scene changes; this is measurably a
ratchet (each re-baseline legitimises accumulated loudness creep:
$0.599\to0.699\to0.823$ over three scenes in one run) and remains a known
limitation.

\paragraph{Boundary smoothing.}
At each audio chunk boundary, a linear blend over $\pm2$ audio latent frames
is applied in latent space before VAE decoding.  This eliminates click
artifacts that arise from the abrupt splice between consecutive chunks,
which would otherwise be visible as discontinuities in the spectrogram.

\subsection{Per-Chunk Overlap Phase-Jitter}
\label{sec:jitter}

The loudness-envelope repetition analysed in Section~\ref{sec:failures}
turned out to live neither in the conditioning values nor in the guidance
weights, but in the \emph{geometry of the chunk grid}.  With a constant
overlap, every continuation chunk denoises a window of identical shape: same
overlap length, same total window length, hence the same split between the
regenerated-and-dropped lead-in and the kept new frames.  The kept region is
therefore always the same phase of the model's window arc --- its canonical
loudness gesture for the static prompt --- and the chunk map acquires a fixed
point: each chunk re-renders the arc and hands the next chunk a context that
elicits the same arc again.  The lock engages exactly when the
reference-audio window first reaches full length (chunk~2--3), which is why
listeners hear the audio ``start repeating after chunk~1''.  This reading
also explains the intervention record of Section~\ref{sec:failures}: every
failed intervention modulated conditioning \emph{values} inside a window
whose \emph{shape} it left untouched, and a fixed point of the window shape
is invisible to all of them.

The fix is to make a fixed point impossible.  The per-chunk overlap cycles
through $[\text{full},\,\text{half},\,\tfrac34]$ of the configured value ---
$[8,4,6]$ latent frames for $\text{overlap}=8$; the realised sequence in the
reported runs is $4,6,8,4,6,8,\dots$ --- so no two consecutive chunks share a
window shape and no single arc phase can be kept twice in a row.  Three
invariants keep the scheme transparent to the rest of the pipeline:

\begin{itemize}[noitemsep]
\item \textbf{Timeline invariance.}  Every chunk still keeps exactly
  $\text{new\_lf}$ video and $\text{new\_af}$ audio frames; only the
  regenerated-and-dropped lead-in varies in length.  The assembled output
  timeline is unchanged relative to a constant-overlap run.
\item \textbf{A/V proportionality.}  The audio overlap derives from the same
  per-chunk video overlap ($34/50/67$\,af for $4/6/8$\,lf in the reported
  runs), so video and audio overlaps scale together and no audio/video
  offset accumulates.
\item \textbf{Buffer slicing.}  The video and audio SLBs are stored at the
  configured maximum overlap; each chunk slices the last $N$ frames matching
  its jittered value, so buffer management is unchanged.
\end{itemize}

The jitter shortens the effective context on half-overlap chunks ($4$\,lf);
no video-continuity loss is measured at the ten-chunk horizon, but longer
horizons are untested (Section~\ref{sec:limitations}).  A structurally
simpler alternative --- re-rendering the audio of the assembled Stage-1
video in a single non-chunked pass --- was implemented and worked for short
clips, but was rejected by design: CLSS exists for arbitrary-length
streaming, and a whole-video audio window reintroduces exactly the
$O(\text{total\_frames})$ context scaling the chunking removes (at this
model's joint audio-video token count it is also VRAM-blocked outright,
$\approx140$k tokens against a 42k budget).  The phase-jitter achieves the
anti-repetition effect chunk-natively, at any length.

\subsection{ComfyUI Node Integration}
\label{sec:nodes}

Five custom nodes implement the full pipeline inside ComfyUI:

\begin{enumerate}[leftmargin=*,noitemsep]
\item \textbf{CLSSConfig}: exposes the CLSS hyperparameters worth exposing
  ($\tau_c, \beta$, overlap); validated internals are fixed.
\item \textbf{CLSSScenePrompts}: multi-scene text input via \texttt{---} delimiters;
  Gemma-enhanced per scene.  Output is a flat CONDITIONING list with one entry
  per scene, proportionally assigned to chunks.  With one prompt per chunk this
  doubles as a per-chunk \emph{object-identity} anchor (see
  Section~\ref{sec:limitations}).
\item \textbf{CLSSStreamingSampler}: Stage 1 streaming sampler.  Accepts any
  ComfyUI GUIDER/SAMPLER/SIGMAS/NOISE/LATENT combination.  Implements the
  per-chunk overlap phase-jitter (Section~\ref{sec:jitter}) and emits an
  unconditional settings dump, per-chunk telemetry, end-of-run trend
  summaries with per-chunk localisation, per-frame origin/layout drift event
  tables, and a phase-lock repetition detector.
\item \textbf{CLSSStage2}: Stage 2 refinement sampler with consistent per-chunk
  noise slicing, per-window detail anchoring, and frozen-audio passthrough
  (Section~\ref{sec:twostage}).
\item \textbf{CLSSAVGuiderV2}: reference-parity multi-modal guider
  (Section~\ref{sec:guider}).  Its predecessor (\textbf{CLSSAVGuider}, a
  \texttt{sampler\_cfg\_function} patch) is retained but inert on current
  ComfyUI and warns accordingly.
\end{enumerate}

All stochastic inputs are seeded: Stage-1 video \emph{and} audio noise are
pre-generated as full-sequence fields sliced per chunk (distinct yet coherent
noise per chunk, bit-reproducible runs), and every fallback noise path uses a
generator derived deterministically from the seed and chunk position.

\subsection{Multi-Modal Guidance and the Packed-Latent Pitfall}
\label{sec:guider}

The reference pipeline guides each modality independently
(\texttt{MultiModalGuider}):
\begin{equation}
\text{pred} = c + (s_{\text{cfg}}-1)(c-u)
             + s_{\text{stg}}\,(c-p)
             + (s_{\text{mod}}-1)(c-m)
\label{eq:guider}
\end{equation}
per modality, followed by a rescale
$\text{pred} \mathrel{*}= r\,\sigma_c/\sigma_{\text{pred}} + (1-r)$,
where $u$ is the text-unconditional prediction, $m$ the modality-isolated
prediction (both audio$\leftrightarrow$video cross-attentions skipped), and
$p$ the STG-perturbed prediction.  The STG perturbation skips
\emph{self}-attention in designated blocks (block 28 for LTX-2.3) by
replacing the attention output with the raw value projection
($\text{out}=W_V x$, gating and output projection unchanged) --- a
value-passthrough, not a zero-out.  The reference defaults are video cfg
4--4.5, audio cfg 7, modality 3, STG 1 for both modalities, rescale 0.7
(four transformer passes per step).  The working configuration runs
$s_{\text{mod}}=1$: the modality term of Eq.~\eqref{eq:guider} vanishes and
its pass is skipped (three passes per step).  This is a measured choice, not
an economy: raising modality guidance to the reference value 3 was tested
live and made the audio audibly \emph{worse} (hiss/drone; within-chunk audio
coherence collapsed $0.68\to0.61$) while leaving the audio repetition it
might have addressed unchanged --- with Stage-2 audio frozen, the raw guided
Stage-1 audio is the final audio, and additional guidance energy surfaces
directly as audible high-frequency content.

\paragraph{The packed-latent representation.}  ComfyUI's
\texttt{CFGGuider.sample()} packs nested audio-video latents into a
\emph{single flat} $[B,1,N_v{+}N_a]$ tensor before sampling and unpacks only
after.  A guider that tries to detect the audio-video case with
\texttt{isinstance(x, NestedTensor)} inside \texttt{predict\_noise} therefore
never sees a nested tensor and falls back to plain shared CFG --- and it does
so silently, producing no error and no log line.  The guider must instead
capture the per-modality shapes in \texttt{sample()} \emph{before} packing,
detect the packed $[B,1,N]$ representation in \texttt{predict\_noise}, unpack
each pass output, apply Eq.~\eqref{eq:guider} per modality, and repack.  Two
diagnostics guard against a silent regression: the guider announces the active
branch and its pass count once per chunk (\texttt{passes/step=3} for the
working configuration, \texttt{4} with modality guidance enabled), and it logs
the STG difference norms so a zero-valued (inert) perturbation is visible
immediately.  A useful invariant follows from the pass count: because each
guidance term costs a transformer pass, a guidance configuration that does not
change per-step wall-clock time is not actually running --- in an earlier
13-lf configuration the four-pass stack cost $\approx17.3$\,s/it against
$\approx8.0$\,s/it for plain CFG.  Two engineering rules generalise: guidance
paths must announce which branch is active, loudly and unconditionally; and a
guidance change that does not change step time did not happen.

%--------------------------------------------------------------------------
\section{Experiments}
\label{sec:experiments}
%--------------------------------------------------------------------------

Two generation experiments share the same CLSS configuration, seed, and active
guidance stack but differ in the first-frame conditioning: a text-to-video
(T2V) run with no image prior (Section~\ref{sec:exp_t2v}), and an
image-to-video (I2V) run conditioned on a single guide frame
($1\times11\times20$ latent, Section~\ref{sec:exp_i2v}).  Both stream ten
Stage-1 chunks ($\text{new\_lf}=16$, $\text{overlap}=8$, jittered
$[4,6,8]$ per chunk, Section~\ref{sec:jitter}) to 160 latent frames
($\approx53$\,s at 24\,fps) and refine through the same four-window Stage~2
pass.

\subsection{Shared Configuration}

\begin{table}[H]
\centering
\caption{Shared configuration.  Guidance values are those actually active during
sampling (verified by the guider's per-chunk \texttt{passes/step} and
difference-norm telemetry, Section~\ref{sec:guider}).  The Stage-2 geometry is
selected automatically from the VRAM token budget.}
\label{tab:config}
\begin{tabular}{ll}
\toprule
Parameter & Value \\
\midrule
Model & LTX-2.3 22B (Q4\_K\_S GGUF) \\
Resolution & $704\times512$ (Stage 1), $1408\times1024$ (Stage 2) \\
$\tau_c$ & 0.05 \\
$\beta$ & 0.40 \\
$\lambda$ & 0.10 \\
$\Delta_\sigma$ & 0.05 \\
$F_a$ & 3 (auto, for 10 chunks) \\
$\boldsymbol\gamma$ & $(0.0,\,0.05,\,0.2,\,0.3)$ \\
Detail anchor & on (Stage 1 scene-first ref; Stage 2 per-window ref) \\
Video guidance & CFG 4.0, STG 1.0 \\
Audio guidance & CFG 7.0, STG 1.0 \\
Modality guidance & 1.0 (disabled; Section~\ref{sec:guider}) \\
STG block / rescale & 28 / 0.70 (three passes/step) \\
S1 noise temporal-corr mix & 0.30 (video only) \\
Audio continuity & audio SLB at $\tau_c$ (auto$\to$on) + \texttt{ref\_audio} 67\,af, clean \\
Overlap jitter & on; cycle $[8,4,6]$ lf (full/half/$\tfrac34$ of 8) \\
Audio anchor & RMS-only, reference-exact $\pm5\%$ \\
Stage 1 steps & 20 \\
Stage 2 steps & 3 (distilled), audio frozen (mask 0) \\
VRAM (GPU) & 15.61\,GB (RTX-class) \\
\midrule
T2V first-frame & Text only \\
I2V first-frame & Guide image, latent $[1,128,1,11,20]$ \\
Stage 1 (both) & 10 chunks, $\text{new\_lf}=16$, $\text{overlap}=8$, 1 scene \\
Stage 2 (both) & 4 windows, $\text{fpc}=40$, $\text{overlap}=13$ (auto) \\
\bottomrule
\end{tabular}
\end{table}

%--------------------------------------------------------------------------
\subsection{Experiment 1: Text-to-Video (T2V)}
\label{sec:exp_t2v}
%--------------------------------------------------------------------------

No image is provided; Stage~1 chunk~1 begins from pure noise conditioned on the
text prompt alone.  The clip is a single prompted scene streamed as ten chunks
($\text{new\_lf}=16$, $\text{overlap}=8$, jittered $[4,6,8]$), assembling to
160 latent frames
($\approx53$\,s), under the identical seed and guidance stack as the I2V run
(Table~\ref{tab:config}).  The prompted content is highly dynamic: intra-chunk
similarity (a chunk's first vs.\ last new frame) stays low-to-moderate
($0.02$--$0.71$) for the whole run
(Table~\ref{tab:t2v_s1_metrics}), so this run exercises the correction
stack under continuous motion rather than a stable anchored scene.

\subsubsection{Guidance Activity}

Every chunk reports \texttt{[CLSS AVGuiderV2] active: video\_cfg=4.0
audio\_cfg=7.0 modality=1.0 stg=v1.0/a1.0@blk[28] rescale=0.70
passes/step=3}, so no step fell back to plain shared CFG.  The guider's
step-1 STG difference norms stay well away from zero on both modalities
throughout --- video $83.8$--$112.7$, audio $20.3$ at chunk~1 rising to
$46$--$53$ by the final chunks --- confirming both STG perturbations are live
on every chunk (a zero norm would mean an inert self-attention skip).  The
mirror-image chunk-1 outlier appears in I2V on the \emph{video} norm instead
(Section~\ref{sec:exp_i2v}), where the guide image is the unmatched
conditioning.

\subsubsection{Stage 1 Results}

\begin{table}[H]
\centering
\caption{T2V Stage 1 per-chunk video metrics (10 chunks).}
\label{tab:t2v_s1_metrics}
\begin{tabular}{ccccc}
\toprule
Chunk & Boundary sim$\uparrow$ & Intra sim & Identity sim & $\rho_{\rm loop}$ \\
\midrule
1/10  & N/A     & 0.0215 & 1.0000 (ref) & 0.570 \\
2/10  & 0.7957  & 0.5740 & 0.7957 & 0.570 \\
3/10  & 0.9185  & 0.2679 & 0.6716 & 0.570 \\
4/10  & 0.7828  & 0.3469 & 0.7828 & 0.570 \\
5/10  & 0.4685  & 0.2626 & 0.5317 & 0.570 \\
6/10  & 0.5408  & 0.3013 & 0.5852 & 0.570 \\
7/10  & 0.8607  & 0.7100 & 0.8607 & 0.570 \\
8/10  & 0.7298  & 0.5166 & 0.7298 & 0.570 \\
9/10  & 0.7801  & 0.2692 & 0.5815 & 0.570 \\
10/10 & 0.7900  & 0.5356 & 0.6698 & 0.570 \\
\bottomrule
\end{tabular}
\end{table}

Without a guide image, video boundary continuity is far more variable than
I2V's: the seams range from $0.469$ (chunk~5) to $0.919$ (chunk~3), with the
weakest hand-offs sitting \emph{mid-run} (chunks 5--6, $0.469$/$0.541$) and
the final three seams holding $0.73$--$0.79$.  The first-to-last trend is
flat ($0.796\to0.790$), so this is boundary \emph{variance}, not accumulated
drift --- the floor does not deepen with chunk index.  Chunk~5's dip
coincides with the first half-overlap window ($4$\,lf context) following a
full-overlap chunk: the jitter (Section~\ref{sec:jitter}) trades a shorter
context on those chunks for its anti-repetition effect, and the cost shows up
here as seam variance rather than as drift.  Intra-chunk similarity stays low
throughout ($0.02$--$0.71$), confirming sustained motion within every chunk.
Origin similarity to the scene reference is contained over the run
($0.161\to0.158$, range $0.107$), and identity similarity to the anchor bank
holds a $0.53$--$0.86$ band with no monotonic decay.  The largest
origin-similarity drops still concentrate at the chunk~1$\to$2 hand-off
(deepest $\Delta=-0.406$ at $t=5.3$\,s, with the next three largest also in
chunks 2--5), while the largest coarse-layout drops spread across chunks 1,
2, 3, 4, and 9 --- consistent with a run whose content moves throughout
rather than drifting from a fixed opening.

\begin{table}[H]
\centering
\caption{T2V Stage 1 AdaIN corrections, band gains, and detail-anchor gains
($g_{\rm lo}/g_{\rm hi}$, Eq.~\eqref{eq:detail}; $0.9000$ is the per-chunk
floor cap).}
\label{tab:t2v_s1_adain}
\begin{tabular}{ccccccc}
\toprule
Chunk & $\Delta\mu$ & $\Delta\sigma$ & $g_1$ & $g_2$/$g_3$ & $g_{\rm lo}$ & $g_{\rm hi}$ \\
\midrule
1  & $+0.0000$ & $+0.0000$ & 1.0000 & 1.0000/1.0000 & ref & ref \\
2  & $-0.0197$ & $-0.0213$ & 0.9962 & 0.9950/0.9929 & 0.9716 & 1.0341 \\
3  & $-0.0100$ & $-0.0133$ & 0.9985 & 0.9889/0.9865 & 1.0027 & 1.0167 \\
4  & $-0.0040$ & $-0.0379$ & 0.9941 & 0.9638/0.9765 & 1.0404 & 0.9361 \\
5  & $-0.0118$ & $-0.0206$ & 0.9942 & 0.9855/0.9965 & 1.0129 & 0.9845 \\
6  & $+0.0025$ & $-0.0128$ & 0.9949 & 0.9784/0.9955 & 1.0483 & 0.9749 \\
7  & $+0.0047$ & $-0.0416$ & 0.9930 & 0.9636/0.9929 & 1.0591 & 0.9176 \\
8  & $+0.0002$ & $-0.0337$ & 0.9927 & 0.9761/0.9954 & 1.0525 & 0.9401 \\
9  & $+0.0047$ & $+0.0036$ & 0.9962 & 0.9922/0.9966 & 1.0758 & 1.0025 \\
10 & $+0.0033$ & $-0.0485$ & 0.9915 & 0.9641/0.9921 & 1.0137 & 0.9181 \\
\bottomrule
\end{tabular}
\end{table}

Every T2V continuation chunk except chunk~9 receives a \emph{downward} std
correction ($\Delta\sigma<0$; chunk~9 is $+0.0036$), in contrast to I2V's
near-neutral pattern (Table~\ref{tab:i2v_s1_adain}): without an
image-conditioned first chunk to compress toward, each text-only chunk's raw
std runs hot relative to the EMA reference and AdaIN consistently pulls it
back down.  Spectral shrinkage is correspondingly more active than in I2V
(band-2 gains down to $0.9636$ vs.\ I2V's $\geq0.983$).  The detail anchor
works visibly hard in this run: raw high-band energy overshoots its
scene-first reference on most chunks from chunk~4 (the model keeps adding
spatial detail energy under sustained motion), pulling $g_{\rm hi}$ down to
$0.918$--$0.940$ while $g_{\rm lo}$ boosts the low band by up to $7.6\%$ ---
the net effect is a high-frequency \emph{share} held exactly at its $0.4863$
reference on every chunk, where the same one-sided shrinkage without the
anchor produced a monotonic hf-share collapse (Section~\ref{sec:detail}).

The anchor bank grows to six entries over the run (bank\_frame\_ids
$=[15,\,47,\,63,\,95,\,111,\,159]$).  With $\text{new\_lf}=16$, chunk $k$'s
last frame lands at absolute index $16k-1$: $15, 31, 47, 63, \dots$ for
$k=1,2,3,\dots$ --- so these six entries are chunks $\{1, 3, 4, 6, 7, 10\}$.
Four of the six are the forced-insertion schedule exactly
($\text{chunk\_index} \bmod F_a = 0$ with $F_a=3$: chunk~1 always seeds, then
chunks 4, 7, 10).  Chunks 3 and 6 are \emph{organic}, threshold-triggered
commits: chunk~2's similarity to the seed anchor was already below threshold
($\text{last\_frame\_max\_sim}=0.6679$, streak$=1$) and chunk~3 pushed the
streak to $P=2$; the same pattern repeats at chunks 5--6
($\text{last\_frame\_max\_sim}=0.6113$ at chunk~5).  Because the forced
positions are fixed by chunk index alone, the two runs' forced entries
coincide exactly despite entirely different video content; the organic
commits are content-dependent, and here T2V commits twice organically while
I2V commits once (chunk~3 in both; I2V's chunk-5 similarity, $0.8621$, stays
above threshold, so its bank stops at five entries,
Section~\ref{sec:exp_i2v}).

\subsubsection{Stage 1 Audio}
\label{sec:t2v_audio}

\begin{table}[H]
\centering
\caption{T2V Stage 1 per-chunk audio metrics.  RMS raw is the chunk's
pre-anchor loudness; RMS out is after the reference-exact anchor
(chunk-1 onset-excluded reference $0.8404$).  SLB hon.\ is the frozen
audio-SLB verification ($1.0$ = the seeded tail survived denoising).}
\label{tab:aud_t2v}
\begin{tabular}{cccccccc}
\toprule
Chunk & WC start & WC end & env\_corr & RMS raw & RMS out & Bnd sim & SLB hon. \\
\midrule
1  & 0.745 & 0.622 & ---      & 0.842 & (ref)  & N/A    & ---   \\
2  & 0.867 & 0.770 & $-$0.510 & 0.835 & 0.840  & 0.8488 & 1.000 \\
3  & 0.695 & 0.826 & $-$0.003 & 0.743 & 0.830  & 0.8693 & 1.000 \\
4  & 0.417 & 0.381 & $-$0.035 & 0.786 & 0.826  & 0.8993 & 1.000 \\
5  & 0.653 & 0.757 & $-$0.135 & 0.824 & 0.826  & 0.7569 & 1.000 \\
6  & 0.637 & 0.715 & $-$0.338 & 0.734 & 0.816  & 0.7243 & 1.000 \\
7  & 0.780 & 0.765 & $-$0.285 & 0.818 & 0.816  & 0.9000 & 1.000 \\
8  & 0.632 & 0.559 & $-$0.194 & 0.761 & 0.811  & 0.8514 & 1.000 \\
9  & 0.648 & 0.705 & $-$0.046 & 0.776 & 0.807  & 0.3915 & 1.000 \\
10 & 0.730 & 0.741 & $-$0.258 & 0.793 & 0.806  & 0.9162 & 1.000 \\
\bottomrule
\end{tabular}
\end{table}

The reference-exact RMS anchor holds output loudness at $0.806$--$0.840$
against raw per-chunk excursions of $0.734$--$0.842$ (largest correction gain
$1.12$, chunk~3) --- the raw collapse-and-creep pattern of the pre-anchor
runs is gone, and the anchor now trims single-digit percentages rather than
rescuing a $+72\%$ drift.  The headline change over every earlier
configuration is the envelope row: env\_corr never rises above $-0.003$ at
any of the nine hand-offs (trend $-0.510\to-0.258$, range $0.507$), where the
matched constant-overlap runs sustained $0.76$--$0.96$ from chunk~4 onward.
The energy-peak detector reads fully scattered (peaks at frames
$[38,\,118,\,127,\,43,\,101,\,64,\,26,\,86,\,49,\,12]$, mode covering $1/10$
within $\pm1$): no shared phase, no recurring gesture --- the fixed-point
mechanism of Section~\ref{sec:jitter} is broken by construction, and the
audible metronome with it.  Boundary similarity with the restored audio SLB
holds $0.72$--$0.92$ on eight of nine seams, rising first-to-last
($0.849\to0.916$); the single weak seam ($0.392$, chunk~9) is flagged by the
trend summary and is the honest residual of this run.  The SLB freeze is
verified numerically at every chunk (\texttt{SLB honored}$=1.0000$
throughout).

\subsubsection{Stage 2 Results}

\begin{table}[H]
\centering
\caption{T2V Stage 2 per-window metrics (4 windows).  $g_{\rm lo}$/$g_{\rm hi}$
are the per-window detail-anchor gains (reference: the window's own upscaled
Stage-1 slice); Aud\_bnd is the frozen Stage-1 audio's own continuity at the
window seam (Stage~2 never re-rolls audio).}
\label{tab:t2v_s2_metrics}
\begin{tabular}{ccccccc}
\toprule
Window & Bnd sim$\uparrow$ & Intra sim & Fid first & Fid last & Aud\_bnd & $g_{\rm lo}$/$g_{\rm hi}$ \\
\midrule
1/4 & N/A    & $-$0.3224 & 0.9190 & 0.9669 & N/A    & 1.036/0.900 \\
2/4 & 0.9509 & 0.5568 & 0.9667 & 0.9277 & 0.7783 & 1.048/0.900 \\
3/4 & 0.5629 & 0.2996 & 0.9280 & 0.9343 & 0.9001 & 1.036/0.900 \\
4/4 & 0.7740 & 0.5562 & 0.8992 & 0.9230 & 0.8311 & 1.021/0.900 \\
\bottomrule
\end{tabular}
\end{table}

Window~1's intra similarity is \emph{negative} ($-0.322$), unlike I2V's
positive $0.728$ for the same window: the dynamic T2V opening
(Table~\ref{tab:t2v_s1_metrics}, chunk-1 intra $0.022$) carries into Stage~2 as a
first window whose start and end frames barely correlate, whereas I2V's guide
image keeps its first window internally coherent.  The per-window detail
anchor engages identically at every window: the 3-step distilled refinement
adds spatial high-frequency energy over its Stage-1 seed at every window
(pre-anchor hf share $0.46$--$0.50$ against Stage-1 references of
$0.32$--$0.35$), and $g_{\rm hi}$ rides its $0.90$ floor cap in all four
windows, pulling the excess back toward the Stage-1 reference.  Because the
reference is recomputed per window, the correction cannot compound: fidelity
to Stage-1 structure holds $0.90$--$0.97$ throughout (fid\_first
$0.919\to0.899$, fid\_last $0.967\to0.923$ first-to-last), with no
end-of-run collapse.  The audio row measures the \emph{frozen} Stage-1
audio's own continuity at the three window seams ($0.778$/$0.900$/$0.831$,
rising with the Stage-1 audio's own improved seams) ---
Stage~2 introduces no audio seams of its own
(\texttt{frozen\_verify\_sim}$=1.0$ at every window).

%--------------------------------------------------------------------------
\subsection{Experiment 2: Image-to-Video (I2V)}
\label{sec:exp_i2v}
%--------------------------------------------------------------------------

A single guide image is encoded to a latent of shape $[1,128,1,11,20]$ and
provided as first-frame conditioning to Stage~1 chunk~1 (guide adherence
$1.0000$ measured at the placed frame).  The clip is a single prompted scene
streamed as ten chunks ($\text{new\_lf}=16$, $\text{overlap}=8$, jittered
$[4,6,8]$), assembling to 160 latent frames ($\approx53$\,s).  All CLSS
hyperparameters and the guidance stack are those of Table~\ref{tab:config}.

\subsubsection{Guidance Activity}

Every chunk reports \texttt{[CLSS AVGuiderV2] active: video\_cfg=4.0
audio\_cfg=7.0 modality=1.0 stg=v1.0/a1.0@blk[28] rescale=0.70
passes/step=3}, so no step fell back to plain shared CFG.  The step-1 STG
difference norms stay well away from zero on both modalities on every chunk
--- video $81.6$--$133.5$, audio $4.9$--$25.0$ --- with chunk~1 the clear
video-side outlier ($203.7$): the guide image is a hard constraint the
self-attention-skipped prediction cannot honour, so the perturbation response
is largest exactly where the conditioning is strongest.

\subsubsection{Stage 1 Results}

\begin{table}[H]
\centering
\caption{I2V Stage 1 per-chunk video metrics (10 chunks).  Boundary\_sim
compares the last overlap frame of the previous chunk against the first new
frame; identity\_sim compares the chunk against its nearest anchor-bank entry.}
\label{tab:i2v_s1_metrics}
\begin{tabular}{ccccc}
\toprule
Chunk & Boundary sim$\uparrow$ & Intra sim$\uparrow$ & Identity sim & $\rho_{\rm loop}$ \\
\midrule
1/10  & N/A     & 0.4934 & 1.0000 (ref) & 0.570 \\
2/10  & 0.7900  & 0.6997 & 0.7900 & 0.570 \\
3/10  & 0.8650  & 0.6752 & 0.7542 & 0.570 \\
4/10  & 0.9586  & 0.8974 & 0.9586 & 0.570 \\
5/10  & 0.9373  & 0.8498 & 0.9373 & 0.570 \\
6/10  & 0.9404  & 0.8175 & 0.8776 & 0.570 \\
7/10  & 0.9713  & 0.9053 & 0.9053 & 0.570 \\
8/10  & 0.9505  & 0.8755 & 0.9505 & 0.570 \\
9/10  & 0.9614  & 0.8622 & 0.8513 & 0.570 \\
10/10 & 0.9814  & 0.7029 & 0.9204 & 0.570 \\
\bottomrule
\end{tabular}
\end{table}

Video boundary continuity holds between $0.790$ and $0.981$ across all nine
chunk transitions and \emph{rises} over the run --- the strongest seam is the
last one.  The floor sits at chunk~2 ($0.7900$), the first SLB-conditioned
hand-off, after which no seam falls below $0.86$: the corrected loop does not
compound error over this horizon, and the jittered context length
($4$--$8$\,lf) does not measurably cost video continuity here.  The largest
structural events of the whole run still cluster at the chunk~1$\to$2 seam
($t\approx5.3$--$6.3$\,s): the four largest per-frame origin-similarity drops
land there (deepest $\Delta=-0.190$), the transition out of the
guide-image-locked opening.  Global origin similarity to the scene reference
is contained over the full run ($0.327\to0.290$, range $0.084$), in contrast
to the monotonic walk-away drift seen at wider overlaps in earlier open-loop
testing.  Identity similarity to the anchor bank dips early (floor $0.754$ at
chunk~3) and recovers to $0.92$, and intra-chunk similarity rises from
$0.49$ to a $0.82$--$0.91$ plateau as the scene settles --- a stable anchored
scene, the complementary regime to T2V's sustained motion.

\begin{table}[H]
\centering
\caption{I2V Stage 1 AdaIN corrections, band gains, and detail-anchor gains
(Band 0 is the DC band, $\gamma_0=0$, gain$\equiv1$, omitted).}
\label{tab:i2v_s1_adain}
\begin{tabular}{ccccccc}
\toprule
Chunk & $\Delta\mu$ & $\Delta\sigma$ & $g_1$ & $g_2$/$g_3$ & $g_{\rm lo}$ & $g_{\rm hi}$ \\
\midrule
1  & $+0.0000$ & $+0.0000$ & 1.0000 & 1.0000/1.0000 & ref & ref \\
2  & $-0.0128$ & $-0.0166$ & 0.9955 & 0.9828/0.9924 & 1.0013 & 0.9782 \\
3  & $-0.0029$ & $-0.0072$ & 0.9969 & 0.9888/0.9926 & 1.0184 & 0.9815 \\
4  & $-0.0052$ & $-0.0121$ & 0.9961 & 0.9874/0.9982 & 1.0120 & 0.9843 \\
5  & $-0.0031$ & $-0.0109$ & 0.9949 & 0.9912/0.9978 & 1.0134 & 0.9894 \\
6  & $-0.0019$ & $-0.0086$ & 0.9949 & 0.9907/0.9957 & 1.0152 & 0.9947 \\
7  & $-0.0032$ & $-0.0094$ & 0.9944 & 0.9920/0.9950 & 1.0209 & 0.9875 \\
8  & $-0.0025$ & $-0.0211$ & 0.9955 & 0.9860/0.9941 & 1.0027 & 0.9732 \\
9  & $+0.0014$ & $-0.0158$ & 0.9964 & 0.9855/0.9940 & 1.0175 & 0.9686 \\
10 & $+0.0002$ & $+0.0054$ & 0.9989 & 0.9938/0.9925 & 1.0413 & 0.9918 \\
\bottomrule
\end{tabular}
\end{table}

On this stable anchored scene the correction stack idles, as designed: AdaIN
deltas stay within $|\Delta\mu|\le0.013$, $|\Delta\sigma|\le0.021$, every band
gain is $\ge0.983$, and the detail-anchor gains never stray more than $4.1\%$
(low band) / $3.1\%$ (high band) from unity --- an every-chunk trim, not a
fight.  The result is the flattest telemetry of either run: high-frequency
share exactly flat at its $0.5090$ reference on every chunk, std stable
($0.967\to0.969$).  Contrast T2V (Table~\ref{tab:t2v_s1_adain}), where the
same stack works measurably harder every chunk; the corrections scale with
measured excess rather than applying a fixed schedule.

The anchor bank grows from 1 to 5 entries over the run at chunks
$\{1,3,4,7,10\}$ (bank\_frame\_ids $=[15,\,47,\,63,\,111,\,159]$) --- the
forced-insertion schedule plus the single organic commit at chunk~3 derived
in detail for T2V (Section~\ref{sec:exp_t2v}).  I2V's second organic
opportunity does not trigger: chunk~5's similarity to the bank ($0.8621$)
stays above the $\rho_a=0.78$ threshold, so its bank ends one entry smaller
than T2V's.

The ComfyUI sampler uses the bank for identity telemetry only: the
retrieval-injection conditioning path of Section~\ref{sec:anchor} is present in
the reference library but not wired into this sampler, so the bank measures
identity drift without correcting it.  Two conditioning wirings have been tried
and both failed (Section~\ref{sec:limitations}): the reference library's own
\texttt{VideoConditionByKeyframeIndex} appends a separate token block and
reproduces the audio corruption documented for the i2v guide path
(Section~\ref{sec:guider}); an in-place low-strength replacement at the first
new frame instead produced visible content morphing, because anchor retrieval
returns the \emph{least}-similar non-redundant anchor and so drags each chunk
back toward content the scene has already moved past.  No safe anchor
conditioning mechanism is currently known; the bank remains diagnostic-only.

\subsubsection{Stage 1 Audio}
\label{sec:i2v_audio}

\begin{table}[H]
\centering
\caption{I2V Stage 1 per-chunk audio metrics.  Within-chunk similarity is
reported at the start and end of each chunk; env\_corr is the loudness-envelope
correlation with the previous chunk ($>0.7$ flags a repeating gesture); RMS
raw/out are pre-/post-anchor (chunk-1 onset-excluded reference $0.5589$);
SLB hon.\ is the frozen audio-SLB verification.}
\label{tab:aud_i2v}
\begin{tabular}{cccccccc}
\toprule
Chunk & WC start & WC end & env\_corr & RMS raw & RMS out & Bnd sim & SLB hon. \\
\midrule
1  & 0.347 & 0.523 & ---      & 0.556 & (ref)  & N/A    & ---   \\
2  & 0.482 & 0.842 & 0.060    & 0.511 & 0.554  & 0.6190 & 1.000 \\
3  & 0.740 & 0.811 & 0.164    & 0.570 & 0.556  & 0.8879 & 1.000 \\
4  & 0.919 & 0.886 & 0.190    & 0.581 & 0.558  & 0.9474 & 1.000 \\
5  & 0.791 & 0.748 & $-$0.081 & 0.663 & 0.569  & 0.8736 & 1.000 \\
6  & 0.838 & 0.787 & 0.167    & 0.617 & 0.574  & 0.8882 & 1.000 \\
7  & 0.828 & 0.720 & $-$0.076 & 0.596 & 0.576  & 0.9554 & 1.000 \\
8  & 0.790 & 0.875 & $-$0.001 & 0.657 & 0.584  & 0.9130 & 1.000 \\
9  & 0.917 & 0.920 & $-$0.057 & 0.615 & 0.587  & 0.9104 & 1.000 \\
10 & 0.732 & 0.710 & $-$0.020 & 0.595 & 0.587  & 0.9183 & 1.000 \\
\bottomrule
\end{tabular}
\end{table}

Loudness is intrinsically stable in this run and the anchor enforces it:
raw per-chunk RMS ranges $0.511$--$0.663$ ($-9\%$/$+19\%$ around the $0.5589$
reference) and the anchored output holds $0.554$--$0.587$, with the largest
corrections \emph{downward} ($14\%$ at chunk~5, where the raw chunk runs
loud).  The loudness-envelope correlation never crosses the $0.7$ repetition
flag --- it never exceeds $0.190$ at any hand-off (trend $0.060\to-0.020$,
range $0.271$), where the matched constant-overlap run arced to $0.844$ ---
and the energy-peak positions scatter across the whole window (frames
$[38,\,74,\,42,\,10,\,107,\,128,\,99,\,69,\,64,\,28]$; mode covers $1/10$
within $\pm1$).  The audio-SLB restoration shows directly in the boundary
column: boundary similarity rises from $0.619$ at the first hand-off to a
$0.87$--$0.96$ band from chunk~3 onward (first-to-last $0.619\to0.918$),
against the $0.07$--$0.53$ of the SLB-off configuration, where every chunk
re-invented its audio.  The SLB freeze is verified at every chunk
(\texttt{SLB honored}$=1.0000$).

\subsubsection{Stage 2 Results}

Stage~2 refines the $2\times$-upsampled latent in four overlapping windows
($\text{fpc}=40$, $\text{overlap}=13$, auto-selected from the 42k-token VRAM
budget) against frozen Stage-1 audio (Section~\ref{sec:twostage}).

\begin{table}[H]
\centering
\caption{I2V Stage 2 per-window metrics (4 windows).  Fid is video fidelity to
the Stage-1 latent (first / last frame of the window); Aud\_bnd is the frozen
Stage-1 audio's own continuity at the window seam; $g_{\rm lo}$/$g_{\rm hi}$
are the per-window detail-anchor gains.}
\label{tab:i2v_s2_metrics}
\begin{tabular}{ccccccc}
\toprule
Window & Bnd sim$\uparrow$ & Intra sim & Fid first & Fid last & Aud\_bnd & $g_{\rm lo}$/$g_{\rm hi}$ \\
\midrule
1/4 & N/A    & 0.7276 & 0.9851 & 0.9589 & N/A    & 1.039/0.900 \\
2/4 & 0.8285 & 0.7634 & 0.9546 & 0.9201 & 0.8588 & 1.044/0.900 \\
3/4 & 0.7604 & 0.6768 & 0.9060 & 0.9699 & 0.7521 & 1.058/0.900 \\
4/4 & 0.8961 & 0.6833 & 0.9425 & 0.9105 & 0.0513 & 1.049/0.900 \\
\bottomrule
\end{tabular}
\end{table}

End-of-window fidelity to the Stage-1 latent holds $0.91$--$0.97$ across all
four windows (fid\_first $0.985\to0.942$, fid\_last $0.959\to0.910$
first-to-last) --- no end-of-run erosion.  As in T2V, the distilled
refinement adds spatial
high-frequency energy at every window (pre-anchor hf share $0.45$--$0.48$
against Stage-1 references of $0.34$--$0.36$) and the per-window detail anchor
pulls it back with $g_{\rm hi}$ at the $0.90$ floor cap throughout; because
each window is referenced to its own Stage-1 slice, the trim cannot
accumulate into progressive softening.  Video seam continuity ranges
$0.76$--$0.90$, weakest at the window-2$\to$3 seam ($t\approx26.7$\,s).  The
audio timeline is bit-identical to Stage~1
(\texttt{frozen\_verify\_sim}$=1.0$ per window); the Aud\_bnd column
re-measures the Stage-1 audio's own continuity where the video windows
happen to cut.  Two of the three readings are strong ($0.859$/$0.752$); the
last window's $0.051$ is the Stage-1 audio's own weak transition at
$t=40.0$\,s surfacing verbatim in the frozen passthrough --- Stage~2 never
re-rolls audio, so it can neither cause nor repair it (the Stage-1 trend
summary flags the corresponding span, Table~\ref{tab:aud_i2v}).  The
assembled refined latents are
$[1,128,160,22,40]$ (video, std $0.916$) and $[1,8,1333,16]$ (audio, frozen),
with no NaN/Inf.

%--------------------------------------------------------------------------
\subsection{Computational Overhead}
%--------------------------------------------------------------------------

\begin{table}[H]
\centering
\caption{Wall-clock timing on a 16\,GB GPU (RTX-class, CPU block-streaming);
s/it ranges span the matched T2V and I2V runs, which agree to within a few
percent at every position.  Stage~1 runs three transformer passes per step
(split CFG, STG); Stage~2 runs a single video refinement pass per window
(audio frozen).  The Stage-1 window length varies per chunk because of the
overlap jitter (Section~\ref{sec:jitter}), and the per-chunk cost tracks it.}
\label{tab:timing}
\begin{tabular}{lccccc}
\toprule
Stage / pass & Chunks & Window (lf) & s/it & Time & Tokens \\
\midrule
S1 (20 steps) & 1        & 16 & 19.0        & $\approx6.3$\,min       & --- \\
S1 (20 steps) & 2, 5, 8  & 20 & 21.5--23.1  & $\approx7.1$--$7.7$\,min each & --- \\
S1 (20 steps) & 3, 6, 9  & 22 & 23.6--23.9  & $\approx7.9$\,min each  & --- \\
S1 (20 steps) & 4, 7, 10 & 24 & 25.0--26.1  & $\approx8.3$--$8.7$\,min each & --- \\
\midrule
S2 video (3 steps) & 1/4   & 40 & 69--70     & $\approx3.5$\,min       & 35{,}200 \\
S2 video (3 steps) & 2--4/4 & 53 & 104--106   & $\approx5.2$\,min each  & 46{,}640 \\
\bottomrule
\end{tabular}
\end{table}

Total generation time: Stage~1 $\approx77$--$78$\,min $+$ Stage~2
$\approx19$\,min, i.e.\ $\approx\mathbf{96}$\,\textbf{min} (T2V) to
$\approx\mathbf{97}$\,\textbf{min} (I2V) for a $\approx53$-second clip.  The
dominant cost driver is the three-pass guidance in Stage~1 --- each denoising
step runs three transformer passes (conditional, unconditional,
STG-perturbed) rather than one.  The per-chunk cost now varies with the
jittered window size (Section~\ref{sec:jitter}): chunk~1 is cheapest
($19.0$\,s/it, $16$ latent frames, no overlap context), and the continuation
chunks step up cleanly with window length --- $21.5$--$23.1$\,s/it at
$20$\,lf, $23.6$--$23.9$ at $22$\,lf, $25.0$--$26.1$ at $24$\,lf --- a
per-chunk timing signature of the jitter itself.  In Stage~2 the
per-window cost rises $\approx50\%$ after window~1 ($69$--$70\to104$--$106$\,s/it)
against a token-count rise of $\approx32\%$: as the run proceeds an
increasing share of the model is pushed to CPU (offloaded weights grow from
$\approx5.7$\,GB to $\approx7.8$\,GB across the pass), so the slowdown is
disproportionate to the token increase and is an offload-pressure effect
rather than a compute-scaling one.

The T2V run costs the same as I2V to within rounding: per-chunk and
per-window s/it match to a few percent at every position (e.g.\ Stage-1
chunk~1: $18.97$\,s/it in both runs; Stage-2 window~2: $103.8$ vs.\
$106.0$\,s/it), confirming that the guide image changes neither the token
count nor the compute cost --- only the conditioning.  The Stage-2
offload-pressure slowdown reproduces at the same windows in both runs,
supporting that it is a property of the refinement pipeline rather than of
run content.

%--------------------------------------------------------------------------
\section{Discussion}
\label{sec:discussion}
%--------------------------------------------------------------------------

\subsection{Effect of Chunk Length and Content Regime}

Both runs used $\text{new\_lf}=16$ ($\approx5.3$\,s per chunk), within the
21-frame safe limit established in earlier open-loop testing, streamed as ten
chunks under the active guidance stack, with the overlap jitter
(Section~\ref{sec:jitter}) varying the context length per chunk
($4$--$8$\,lf).  In neither run does boundary
similarity degrade with chunk index.  I2V \emph{improves} monotonically in
the large: its floor is the first SLB-conditioned hand-off ($0.7900$,
chunk~2) and its strongest seam is the last ($0.9814$).  T2V is flat
first-to-last ($0.796\to0.790$) with the weakest seams mid-run ($0.469$ at
chunk~5, $0.541$ at chunk~6) rather than late: where continuity is weak, it
is weak as isolated seam variance --- chunk~5 is the first half-overlap
($4$\,lf) window following a full-overlap chunk --- not as compounding drift.
The two runs exercise
opposite content regimes --- I2V a stable anchored scene (intra-chunk
similarity plateauing at $0.82$--$0.91$), T2V sustained motion (intra
$0.02$--$0.71$ throughout) --- and the correction stack scales with the measured
excess: near-idle on I2V (all band gains $\ge0.983$, detail-anchor gains
within $+4\%$/$-3\%$ of unity) versus working measurably harder on T2V
(band-2 gains to $0.9636$, $g_{\rm hi}$ down to $0.918$ against the raw
high-band overshoot).

\subsection{Identity Tracking and Boundary Self-Consistency}

Chunk~2's identity\_sim (0.7900) equals its boundary\_sim exactly.  This is not a
coincidence but a \emph{self-consistency check}: the anchor was seeded from
chunk~1's last frame, and the SLB passes that same frame as the first latent
frame of chunk~2's conditioning, so the anchor query and the boundary query
compare the same source frame (chunk~1 frame~15) against the same target frame
(chunk~2 frame~0).  Both metrics agreeing validates that the anchor bank and the
SLB operate on the same reference, and that the $\tau_c$ re-noising at the
boundary introduces only minimal distributional shift.  For later chunks the
bank holds multiple entries and the identity query selects a different anchor
than the boundary, so the two metrics diverge, as expected (e.g.\ I2V chunk~6:
identity 0.878 vs boundary 0.940).  The same self-consistency check holds in
the unrelated T2V run at the same chunk (identity $0.7957=$ boundary $0.7957$,
Table~\ref{tab:t2v_s1_metrics}), confirming the mechanism is a property of the
anchor/SLB bookkeeping rather than of any particular content.

\subsection{Audio Coherence and the Role of Visual Context}

A natural hypothesis is that a guide image shapes streaming audio behaviour:
in LTX-2.3's joint audio-video transformer, video and audio tokens share
self-attention layers, so a strong single-frame visual prior could constrain
audio generation implicitly through cross-modal attention --- for better
(a coherence anchor) or worse (a repetition template).  The matched pair does
not support the hypothesis in either direction.  Chunk-1 audio coherence
differs without any guide-image effect to attribute it to (T2V
$0.745\to0.622$ vs.\ I2V $0.347\to0.523$), and with the envelope repetition
now eliminated in \emph{both} modes by the jitter (env\_corr $\le-0.003$
throughout in T2V, $\le0.190$ in I2V; Section~\ref{sec:jitter}), there is no
repetition signature left for the guide image to modulate either.  The
remaining audio differences track the prompted \emph{sound content} --- T2V's
loud continuous ambience (RMS reference $0.8404$) naturally self-correlates
within and across chunks, while I2V's quieter, more varied scene audio (RMS
reference $0.5589$) does not --- rather than the presence or absence of a
visual prior.  The practical conclusion is negative but useful: visual
conditioning is not a lever on streaming audio behaviour at this scale, and
the audio failure modes of Section~\ref{sec:failures} had to be --- and were
--- addressed in the audio path itself.

\subsection{Stability Margin}

With $\rho_{\text{loop}} = 0.570$, the CLSS feedback loop provides a $\approx43\%$
gain reduction per chunk before accounting for the model's open-loop gain $g$.
In the I2V run the spectral-shrinkage correction was light throughout ---
band-2/3 gains of $0.983$--$0.998$, a $\approx1$--$2\%$ high-frequency energy
excess over the EMA reference.  Taking the typical $\approx1$--$2\%$ per-chunk
growth as a rough estimate of the open-loop gain in the spectral channel gives
$g\approx1.02$ and $\rho_{\text{closed}} \approx 0.57\times1.02 \approx 0.58$,
comfortably below the stability boundary of~1.  The T2V run runs hotter on
this channel: band-2 gains fall to $0.964$--$0.985$ for most chunks, a
$\approx2$--$4\%$ typical excess, giving $g\approx1.04$ and
$\rho_{\text{closed}}\approx0.57\times1.04\approx0.59$ --- still comfortably
stable, and close enough to the I2V estimate that the margin appears to be a
property of the correction stack rather than of the conditioning mode.  The
raw audio spectral channel, not covered by the video-side machinery of
Sections~\ref{sec:shrink} and~\ref{sec:detail}, is much improved over the
pre-jitter runs but remains the least-corrected one: the Stage-1 trend
summary's \texttt{aud\_hf} statistic (high-band audio energy relative to the
chunk-1 reference) now \emph{declines} in T2V ($0.885\to0.772$; the residual
energy excess concentrates in the lowest frequency bin instead, up to
$1.62\times$ reference) and grows only mildly in I2V ($0.881\to1.047$, range
$0.360$, with top bins individually reaching $\approx1.9\times$ reference at
chunk~5) --- against the unbounded $0.42\to1.33$ (T2V) and $0.87\to1.28$
(I2V) growth of the constant-overlap, SLB-off runs.  The RMS anchor
constrains only global loudness; no current correction targets the audio
frequency distribution (Section~\ref{sec:failures}).

\subsection{Stage-2 Identity Metric Ambiguity}

Stage~2 lacks an anchor bank; its identity\_sim reduces to comparing each window
against the fixed first-window reference.  On a single moving scene this
conflates ordinary content motion with drift: in I2V, where the reference is the
guide-image region, windows 2--4 sit at a $0.51$--$0.53$ plateau, reflecting that
the video has moved away from its opening frames, not instability.  In T2V,
where window~1 has no anchor to begin with, the same comparison instead
oscillates around zero ($-0.36$ to $+0.06$ across windows~2--4) ---
consistent with window~1 itself being internally uncorrelated
(Table~\ref{tab:t2v_s2_metrics}, intra $-0.322$), so there is no stable
reference for later windows to be ``close to'' or ``far from'' in the first
place.  Adding a scene-aware anchor bank to Stage~2 would make this metric
interpretable in either conditioning mode; as reported it should be read only as
``distance from the opening,'' not as a drift signal.

\subsection{Measured Failure Modes at Longer Horizons}
\label{sec:failures}

Per-frame telemetry across extended runs --- including the ten-chunk,
$\approx53$-second T2V and I2V runs reported above and earlier 13-lf and
31-lf runs --- exposed two repetition mechanisms with distinct signatures.
One is now diagnosed and solved; the other remains open.

\paragraph{Loudness-envelope repetition: diagnosed and solved.}
Earlier Stage-1 configurations repeated a per-chunk loudness gesture:
env\_corr crossed the $0.7$ repetition flag in both conditioning modes
(sustained $0.76$--$0.96$ in T2V; an arc to $0.844$ in I2V), it was the
flagged drift of both trend summaries, and the repetition was audible in
listening across every configuration tested.  Every intervention available at
the conditioning and guidance level was tested live against it, and
\emph{all failed}: enabling the audio SLB under a constant overlap
(repetition unchanged, plus high-frequency runaway $1.02\to1.51$ as the
buffer froze each chunk's loud tail forward); raising modality guidance to
the reference value (repetition unchanged, plus audible hiss/drone as
guidance energy rose); and perturbing the reference-audio window itself ---
blending in noise, decaying its length over chunks, flattening its loudness
envelope (repetition unchanged in each case, with the energy-injecting
variants adding hiss).  Those failures are retained here as the diagnostic
they turned out to be: if no change to conditioning \emph{values} or guidance
\emph{weights} touches the artefact, the artefact must live in the one thing
none of the interventions changed --- the \emph{shape} of the chunk window.
With a constant overlap, every continuation chunk denoises an identical
window and keeps the same phase of the model's window arc, so the arc is a
fixed point of the chunk map (Section~\ref{sec:jitter}); the lock engages
when the reference-audio window reaches full length at chunk~2--3, matching
the user-audible ``audio repeats after chunk~1''.  The per-chunk overlap
phase-jitter breaks the fixed point by construction, and with the lock gone
the audio SLB is safe to restore as the content-continuity carrier.  In the
reported runs the signature is absent: env\_corr never exceeds $-0.003$
(T2V) or $0.190$ (I2V) at any hand-off, the peak-phase detector scatters
($1/10$ mode coverage in both runs), boundary similarity holds a
$0.85$--$0.92$ typical band with the SLB honored at $1.0000$ throughout, and
the restored SLB shows no runaway (T2V \texttt{aud\_hf} $0.885\to0.772$).  A
full-video single-pass audio re-render was also implemented and worked for
short clips, but was rejected by design --- CLSS exists for arbitrary-length
streaming, and a whole-video window defeats it
(Section~\ref{sec:jitter}).

\paragraph{Chunk-relative phase lock, broken by construction.}  An
earlier symptom of the same mechanism was a hard \emph{phase} lock: the audio
energy peak at $94\%$ of the window for eight consecutive 13-lf chunks, and
looser but persistent clustering under constant-overlap 16-lf runs.  With the
jitter, no phase can recur: the detector reads fully scattered in both
reported runs (audio peak mode covering $1/10$ chunks within $\pm1$; T2V
peaks $[38,\,118,\,127,\,43,\,101,\,64,\,26,\,86,\,49,\,12]$, I2V peaks
$[38,\,74,\,42,\,10,\,107,\,128,\,99,\,69,\,64,\,28]$), and env\_corr
confirms the gesture itself is gone, not merely re-phased.

\paragraph{A $\sim$4-second video layout oscillation.}  Coarse scene layout
departs from the scene reference and partially returns with a $\approx4$\,s
wall-clock period that is \emph{invariant to chunk length}: at 13-lf ($4.3$\,s)
chunks the dip lands at new-frame 5--7 in every chunk (appearing seam-locked),
while at 31-lf ($9.9$\,s) chunks it recurs within the chunk at the same
seconds-period.  Context strength and context length (overlap 3/5/8) were tested
and neither removes it; the oscillation appears intrinsic to the model's trained
temporal horizon.  In the reported 16-lf jittered runs the layout-argmin
detector reads unlocked in both modes (T2V mode~4 covering $5/10$ chunks
within $\pm1$, I2V mode~12 covering $4/10$) --- the strict per-chunk
swing-and-return does not phase-lock to the seam grid, though global layout
still wanders (largest per-frame layout drops of $-0.67$ in both runs, spread
across the run rather than concentrated at one seam).  This failure mode
remains open.

\paragraph{Stage-2 audio is frozen by design.}  The freeze
(Section~\ref{sec:twostage}) is the outcome of a measured escalation.  With
per-window audio re-rendering at high denoise ($\sigma$-scale $1.0$),
$\approx45\%$ of the audio is re-rolled per window and the re-rolls disagree
at every window boundary (boundary cosine $0.32$--$0.42$) \emph{regardless}
of the audio SLB length --- the SLB pins the seam frame, not the style of
the re-roll.  At denoise $0.4$ the pass polishes instead (seed similarity
$0.79$--$0.81$) yet seams still disagreed at $0.59$--$0.72$: polishing
narrows the disagreement but cannot close it while windows are denoised
independently.  Freezing (mask 0) closes it exactly --- Stage~2 introduces
no audio seams at all, and the only audio discontinuities in the final
output are Stage~1's own chunk boundaries.  Rule: audio is either generated
in one window or not re-rolled at all; any multi-window audio denoise
re-seams the timeline it was meant to improve.

\paragraph{Audio high-frequency growth, mostly closed.}  The trend-summary's
\texttt{aud\_hf} statistic (high-band audio energy relative to the chunk-1
reference) grew unboundedly in the pre-jitter runs ($0.42\to1.33$ T2V,
$0.87\to1.28$ I2V), and under a constant overlap the audio SLB made it worse
($1.02\to1.51$).  In the reported jittered, SLB-on runs the channel is
closed in T2V ($0.885\to0.772$) and reduced to a mild residual in I2V
($0.881\to1.047$, range $0.360$; top bins to $\approx1.9\times$ reference at
chunk~5).  No current correction targets this channel directly: the
video-side spectral shrinkage
(Section~\ref{sec:shrink}) and detail anchor (Section~\ref{sec:detail})
operate on the video latent only, and the audio-side RMS anchor
(Section~\ref{sec:audio}) constrains global loudness but not the frequency
distribution.  An audio-side two-band anchor, mirroring
Section~\ref{sec:detail} but applied to the audio latent's frequency axis, is
the natural next mechanism to try; an earlier attempt at audio high-band
shrinkage was reverted for audible artefacts, so any such correction must be
validated by ear, not by the statistic it improves.

%--------------------------------------------------------------------------
\section{Limitations}
\label{sec:limitations}
%--------------------------------------------------------------------------

\paragraph{Single hyperparameter configuration, single seed.}
The reported T2V and I2V results share one set of hyperparameters
($\text{new\_lf}=16$, $\text{overlap}=8$, 10 chunks, 1 scene), one seed, and one
hardware configuration (16\,GB VRAM, RTX-class); they differ only in the
first-frame conditioning, by design, to isolate that variable.  No baseline
comparison against open-loop streaming is reported, and no ablation of the
individual CLSS components (re-noising alone, AdaIN alone, shrinkage alone,
anchor bank alone) or of the individual guidance terms (split CFG, modality,
STG) has been performed.  The paper therefore cannot quantify the marginal
contribution of each correction or guidance term, or demonstrate improvement
over the open-loop baseline from the same metrics, and every single-run
comparison in Section~\ref{sec:discussion} (e.g.\ the T2V/I2V
content-regime contrast) is a $n=1$-per-arm observation, not a statistically powered
result.  These comparisons are left to future work.

\paragraph{Stability metrics vs.\ perceptual quality.}
The reported metrics---boundary cosine similarity, intra-chunk cosine similarity,
audio within-chunk segment similarity---measure the \emph{stability} of the
latent representation across chunks.  They do not assess the perceptual quality
of the generated content, prompt adherence, or realism.  Standard quality metrics
(FID, IS, CLIP similarity, human evaluation) would be required to characterise
the generated video as a content generation system.  High boundary similarity is
a necessary but not sufficient condition for high video quality.

\paragraph{Object-level identity is unobserved.}
Every reported metric is computed from mean-pooled channel features or
low-band spatial maps and is therefore \emph{object-blind}: a vehicle or
person can be replaced by a different instance across a chunk boundary while
boundary and identity cosines remain above $0.95$.  This failure class was
observed perceptually and is invisible to the telemetry.  High-similarity
readings must not be interpreted as object persistence.  The available
mitigation is textual: one prompt per chunk via \texttt{CLSSScenePrompts},
re-describing the persistent objects explicitly.  Object-level tracking
metrics (detection/re-identification on decoded frames) are future work.

\paragraph{Stability model assumptions; $g_{\rm SLB}$ not yet measured.}
The linear gain model in Section~\ref{sec:stability} assumes that $g$ is
approximately constant and that the AdaIN and re-noising corrections act as
independent multiplicative attenuators.  Both assumptions simplify the analysis:
the actual closed-loop dynamics involve higher-order interactions between
corrections, guidance, and scene content.  A more rigorous treatment (e.g.,
Lyapunov stability for the latent iteration, or a Monte Carlo sweep over
perturbation seeds and chunk positions) would require characterising the
denoiser's Jacobian across a distribution of latent inputs, and is left to
future work.  Concretely: the $g_{\rm SLB}$ perturbation protocol
(Eq.~\ref{eq:gslb}) is implemented and verified at the tensor level --- the
perturbation is confined exactly to the overlap region, and the norm-ratio
formula recovers a known injected gain in a synthetic test --- but it doubles
per-chunk compute, so it is compiled off in the node (no exposed toggle) and
has not been exercised against a live transformer.  Neither reported
experiment used it: the $g\approx1.02$--$1.05$ figures in
Section~\ref{sec:discussion} remain an informal band-energy proxy, not this
measurement.  Re-enabling it in code for a dedicated measurement run is the
direct next step toward an empirically grounded, rather than assumed, value
of $g$.

\paragraph{No working anchor-bank conditioning.}
The anchor bank tracks long-range identity but does not condition generation:
both wirings attempted to date have failed.  The reference library's
append-style \texttt{VideoConditionByKeyframeIndex} reproduces the AV audio
corruption already diagnosed for the i2v guide path (Section~\ref{sec:guider}).
A low-strength in-place replacement at the first new frame --- verified in
isolation to place the anchor correctly and leave the SLB region untouched ---
was exercised in a full run and produced visible content \emph{morphing}: it
injected a past keyframe into every chunk, and because retrieval returns the
least-similar non-redundant anchor, it dragged each chunk back toward content
the scene had already moved past (one chunk was pulled to an earlier anchor
than a previous chunk had used).  It was reverted.  Conditioning the joint
audio-video model on a temporally-displaced keyframe without either corrupting
audio (append) or morphing video (in-place replace) is an unsolved design
problem; the $\sim$4-second video layout oscillation (Section~\ref{sec:failures})
that motivated the attempt remains unaddressed.

\paragraph{Phase-jitter caveats.}
The overlap jitter (Section~\ref{sec:jitter}) is validated at the
ten-chunk, $\approx53$-second horizon.  (a)~Half-overlap chunks carry only
$4$\,lf of context: no video-continuity loss attributable to the shortened
context is measured at this horizon (the T2V mid-run seam floor of $0.469$
recovers on the following chunks and the trend is flat).  Longer horizons
are simply not tested yet --- the limiting factor is the hardware budget
available for this work (each $\approx53$-second clip costs
$\approx$96--97\,min on a single 16\,GB GPU), not any known property of the
method; longer runs are planned once better hardware is available.
(b)~The jitter cycle is fixed
($[\text{full},\,\text{half},\,\tfrac34]$), not content-adaptive; a schedule
that reacts to measured envelope correlation is unexplored.  (c)~I2V audio
high-frequency energy still grows mildly over the run ($0.881\to1.047$;
Section~\ref{sec:failures}).  (d)~The I2V Stage-2 last-window
\texttt{aud\_bnd} of $0.051$ is the Stage-1 audio's own weak transition at
$t=40.0$\,s surfacing verbatim in the frozen passthrough --- a limitation of
the Stage-1 audio at that span, not of the refinement pass, which never
re-rolls audio.

\paragraph{Hardware specificity.}
The GGUF 4-bit quantisation and CPU block-streaming configuration was designed
for a specific VRAM budget (16\,GB).  Performance, latency, and numerical
behaviour may differ on GPUs with more VRAM (where block-streaming is
unnecessary) or with different quantisation schemes (e.g., Q8 or FP8).

%--------------------------------------------------------------------------
\section{Related Work}
\label{sec:related}
%--------------------------------------------------------------------------

\paragraph{Long video generation.}
StreamingT2V~\cite{henschel2024streamingt2v} and FIFO-Diffusion~\cite{kim2024fifo}
generate long videos by sliding-window denoising.  Gen-L-Video~\cite{wang2023gen}
uses temporal attention patching.  FreeNoise~\cite{qiu2024freenoise} reschedules
the initial noise (window-based fusion of a shuffled, reused noise sequence)
to extend a pretrained model's temporal attention window without retraining or
sliding-window denoising at all --- a tuning-free approach to the same
underlying problem (fixed training-time context length) that CLSS addresses by
chunking with closed-loop correction instead.  VidToMe~\cite{li2024vidtome}
merges self-attention tokens across frames to improve temporal consistency in
zero-shot video editing, operating within a single generation pass rather than
across autoregressively-generated chunks.  CLSS differs from all of these by
applying closed-loop corrections specifically designed for the latent-streaming
regime of large audio-video models, where each chunk is a genuinely separate
denoising process conditioned on the previous chunk's output --- the
exposure-bias setting FreeNoise and VidToMe do not target.

\paragraph{Exposure bias in diffusion.}
The exposure bias problem in autoregressive models is well-studied~\cite{bengio2015scheduled}.
For diffusion models, Ning et al.~\cite{ning2023elucidating} and
Salimans \& Ho~\cite{salimans2022progressive} address related distributional
mismatch issues during training, but inference-time corrections for streaming
have received less attention.

\paragraph{Statistical normalisation for consistency.}
Adaptive Instance Normalisation (AdaIN)~\cite{huang2017arbitrary} was introduced
for style transfer, where the goal is to match the mean and standard deviation of
a content feature map to those of a style reference.  EMA-based statistical
normalisation across video frames has also appeared in temporal consistency methods.
In CLSS, AdaIN is repurposed as a \emph{drift correction} applied to denoised
latents between chunks, using the cross-chunk EMA as the style reference.  The
combination of EMA tracking with AdaIN blending (rather than full replacement) is
motivated by the streaming setting, where the reference must itself evolve to allow
intentional scene changes.

\paragraph{Frequency-domain video editing.}
Yang et al.~\cite{yang2024fresco} and Ceylan et al.~\cite{ceylan2023pix2video}
use frequency-domain constraints for temporal consistency in video editing.  CLSS applies frequency
shrinkage in the \emph{latent} domain to a streaming generation setting, targeting
energy accumulation rather than pixel-domain flicker.

%--------------------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}
%--------------------------------------------------------------------------

We presented CLSS, a five-component closed-loop streaming synthesis framework
that enables stable long audio-video generation with LTX-2.3 22B on consumer
16\,GB VRAM hardware.  The corrections --- calibrated context re-noising,
EMA-tracked AdaIN, frequency-band soft shrinkage, a dynamic anchor bank, and a
two-band spatial detail anchor --- achieve $\rho_{\text{loop}}=0.570$; driven
by a reference-parity multi-modal guider (split per-modality CFG and STG) that
correctly handles ComfyUI's packed audio-video latent representation, the
pipeline held Stage~1 video boundary similarity on a rising trajectory
($0.79\to0.98$ I2V) across ten chunks of matched $\approx53$-second
single-scene clips, held the
high-frequency energy share flat end-to-end in both conditioning modes, and
held audio loudness to its chunk-1 reference within $\pm5\%$ throughout.  A
two-stage pipeline (streaming Stage~1 + windowed distilled Stage~2
with per-window detail anchoring and frozen audio) delivers a fully refined
$2\times$-resolution audio-video output in $\approx96$--$97$ minutes per clip
on a single 16\,GB GPU, essentially independent of conditioning mode.

The headline audio result is that the per-chunk loudness-envelope repetition
--- the metronome that earlier versions of this paper characterised as
structural and immune to intervention --- is diagnosed and solved.  The
diagnosis: the repeated gesture is a \emph{fixed point of the constant-shape
chunk grid}, not a property of any conditioning value, which is why every
conditioning- and guidance-level intervention failed against it.  The fix is
chunk-native: a per-chunk overlap phase-jitter (cycling
$[\text{full},\,\text{half},\,\tfrac34]$ of the configured overlap, so no two
consecutive chunks share a window shape) breaks the fixed point by
construction, and with the phase lock gone the audio SLB is restored as the
content-continuity carrier and the RMS anchor keeps energy stability.  Against
the matched pre-jitter runs, envelope correlation drops from a sustained
$0.76$--$0.96$ to $\le0.19$ at every hand-off ($-0.51$--$0.19$ across both
runs), audio boundary similarity rises
from $0.07$--$0.53$ to a $0.85$--$0.92$ typical band with the SLB verified
honored at every chunk, phase-lock detectors read fully scattered ($1/10$
mode coverage in both runs), and audio high-frequency growth is closed in T2V
($0.885\to0.772$) with a mild residual in I2V ($0.881\to1.047$) ---
all while preserving arbitrary-length streaming, an unchanged output
timeline, and exact audio/video proportionality.

Running matched T2V and I2V generations under an identical seed and guidance
stack, differing only in the presence of a guide image, shows that visual
conditioning is not a lever on streaming audio behaviour: chunk-1 audio
coherence, envelope statistics, and loudness stability all track the prompted
sound content rather than the guide image, while the guide image's clear
effects are on the video side (a stable anchored scene with a rising
$0.79\to0.98$ boundary trajectory versus T2V's variable $0.47$--$0.92$ seams
under sustained motion).  One repetition mechanism remains open at this
horizon: a chunk-length-invariant $\approx4$-second video layout oscillation
that appears intrinsic to the model's trained temporal window (its detector
reads unlocked in both reported runs, but global layout still wanders).  All
of this is visible in the pipeline's per-chunk telemetry ---
unconditional settings dumps, drift-event tables, and a phase-lock detector
--- which is designed to localise such effects in wall-clock time and
latent-frame position, and to make a silently inactive guidance path
impossible to miss (a guidance term that does not change per-step wall-clock
time is not running).

Object-level identity persistence across chunk boundaries, invisible to the
current structural metrics in both conditioning modes, remains the principal
open problem for content-level quality.

%--------------------------------------------------------------------------
\section*{Acknowledgements}
%--------------------------------------------------------------------------
We thank the LTX-Video team at Lightricks for releasing LTX-2.3 and the
associated GGUF weights, and the ComfyUI community for infrastructure.

%--------------------------------------------------------------------------
\bibliographystyle{plain}
\begin{thebibliography}{99}

\bibitem{qiu2024freenoise}
H.~Qiu, M.~Xia, Y.~Zhang, Y.~He, X.~Wang, Y.~Shan, and Z.~Liu.
\newblock {FreeNoise}: Tuning-free longer video diffusion via noise rescheduling.
\newblock In \emph{ICLR}, 2024.

\bibitem{li2024vidtome}
X.~Li, C.~Ma, X.~Yang, and M.-H.~Yang.
\newblock {VidToMe}: Video token merging for zero-shot video editing.
\newblock In \emph{CVPR}, 2024.

\bibitem{henschel2024streamingt2v}
R.~Henschel, L.~Khachatryan, D.~Hayrapetyan, H.~Poghosyan, R.~Abrahamyan,
A.~Nersisyan, S.~I.~Yeranosyan, and O.~Kacher.
\newblock {StreamingT2V}: Consistent, dynamic, and extendable long video generation from text.
\newblock \emph{arXiv:2403.14773}, 2024.

\bibitem{kim2024fifo}
J.~Kim, J.~Jeong, S.~Park, M.~Kim, S.~Kim, and J.~Ye.
\newblock {FIFO-Diffusion}: Generating infinite videos from text without training.
\newblock \emph{arXiv:2405.11473}, 2024.

\bibitem{wang2023gen}
F.~Wang, W.~Chen, G.~Song, H.~Zhang, W.~Li, C.~Shen, and T.~Mei.
\newblock Gen-{L}-Video: Multi-text conditioned long video generation via temporal co-denoising.
\newblock \emph{arXiv:2305.18264}, 2023.

\bibitem{bengio2015scheduled}
S.~Bengio, O.~Vinyals, N.~Jaitly, and N.~Shazeer.
\newblock Scheduled sampling for sequence prediction with recurrent neural networks.
\newblock In \emph{NeurIPS}, 2015.

\bibitem{ning2023elucidating}
M.~Ning, M.~Li, J.~Su, A.~A.~Salah, and I.~Ertugrul.
\newblock Elucidating the exposure bias in diffusion models.
\newblock \emph{arXiv:2308.15321}, 2023.

\bibitem{salimans2022progressive}
T.~Salimans and J.~Ho.
\newblock Progressive distillation for fast sampling of diffusion models.
\newblock In \emph{ICLR}, 2022.

\bibitem{huang2017arbitrary}
X.~Huang and S.~Belongie.
\newblock Arbitrary style transfer in real-time with adaptive instance normalization.
\newblock In \emph{ICCV}, 2017.

\bibitem{yang2024fresco}
S.~Yang, Y.~Zhou, Z.~Liu, and C.~C.~Loy.
\newblock {FRESCO}: Spatial-temporal correspondence for zero-shot video translation.
\newblock In \emph{CVPR}, 2024.

\bibitem{ceylan2023pix2video}
D.~Ceylan, C.-H.~Huang, and N.~J.~Mitra.
\newblock {Pix2Video}: Video editing using image diffusion.
\newblock In \emph{ICCV}, 2023.

\end{thebibliography}

\end{document}
